\chapter{The Derived Category}

\section{Introduction}
Let $\mathcal{A}$ and $\mathcal{B}$ be abelian categories, and let $F\colon \mathcal{A}\to\mathcal{B}$ be a functor. Our purpose is to define, functorially for each $X\in\operatorname{Ob}\mathcal{A}$, a complex $\DerR F(X)$ whose cohomology groups are the right derived functors of $F$ acting on $X$, namely $\RR ^iF(X)$. In general, we will define $\DerR F(X^\bullet)$ for any complex $X^\bullet$ of objects of $\mathcal{A}$.

More precisely, $\DerR F$ will be a functor from the derived category $\DD(\mathcal{A})$ of $\mathcal{A}$ to the derived category $\DD(\mathcal{B})$ of $\mathcal{B}$.

The derived category $\DD(\mathcal{A})$ is obtained as follows: one first considers the category $\KK(\mathcal{A})$, whose objects are complexes of elements of $\mathcal{A}$, and whose morphisms are homotopy equivalence classes of morphisms of complexes. The category $\DD(\mathcal{A})$ is obtained by ``localizing'' $\KK(\mathcal{A})$ so that every morphism in $\KK(\mathcal{A})$ which induces an isomorphism on cohomology becomes an isomorphism in $\DD(\mathcal{A})$. This process of localization will be explained in general below.

Although $\mathcal{A}$ and $\mathcal{B}$ above are assumed to be abelian categories, the categories $\KK(\mathcal{A})$, $\DD(\mathcal{A})$, etc., are in general not abelian. However, they can be given a structure which carries enough information for our purposes, namely a structure of triangulated category. Thus we will be led to study triangulated categories.

\section{Triangulated Categories}
\subsection{Definition}
A triangulated category is an additive category $\mathcal{C}$, together with
\begin{enumerate}
	\item[a)] an automorphism $T\colon \mathcal{C}\to\mathcal{C}$ called the \emph{translation functor}, and
	\item[b)] a collection of sextuples $(X,Y,Z,u,v,w)$, called the \emph{triangles} of $\mathcal{C}$,
\end{enumerate}
where in each sextuple $X,Y,Z\in\operatorname{Ob}\mathcal{C}$ and
\[
u\colon X\to Y,\quad v\colon Y\to Z,\quad w\colon Z\to T(X)
\]
are morphisms. A triangle is usually written
\[
\begin{tikzcd}
	X \arrow[r, "u"] & Y \arrow[d, "v"] \\
	& Z \arrow[ul, "w"]
\end{tikzcd}
\]


A morphism of triangles
\[
(X,Y,Z,u,v,w)\to(X',Y',Z',u',v',w')
\]
is a commutative diagram
\[
\begin{CD}
	X @>u>> Y @>v>> Z @>w>> T(X) \\
	@VfVV @VgVV @VhVV @VT(f)VV \\
	X' @>u'>> Y' @>v'>> Z' @>w'>> T(X')
\end{CD}
\]

This data is subject to the following axioms:

\begin{enumerate}
	\item[\textbf{(TR1)}]
	\begin{enumerate}
		\item Every sextuple isomorphic to a triangle is a triangle.
		\item Every morphism $u\colon X\to Y$ can be embedded in a triangle.
		\item The sextuple $(X,X,0,\operatorname{id}_X,0,0)$ is a triangle.
	\end{enumerate}
	
	\item[\textbf{(TR2)}]
	$(X,Y,Z,u,v,w)$ is a triangle if and only if $(Y,Z,T(X),v,w,-T(u))$ is a triangle.
	
	\item[\textbf{(TR3)}]
	Given two triangles $(X,Y,Z,u,v,w)$ and $(X',Y',Z',u',v',w')$, and morphisms $f\colon X\to X'$, $g\colon Y\to Y'$ such that $u'f=gu$, there exists a morphism $h\colon Z\to Z'$ (not necessarily unique) so that $(f,g,h)$ is a morphism of triangles.
	
	\item[\textbf{(TR4)}] (The octahedral axiom.)\\
	\begin{center}
	\begin{tikzcd}
		& Y' \arrow[dr, dashed, "g"] & \\
		Z' \arrow[ur, dashed, "f"] \arrow[d] & & X' \arrow[ll, "T(j)i"] \arrow[d] \\
		X \arrow[rr, "vu"] \arrow[dr, "u"'] \arrow[uur, "j" near start] & & Z \arrow[u] \arrow[dl, "v"'] \arrow[uul, "i" near start] \\
		& Y \arrow[uul] \arrow[uur] & 
	\end{tikzcd}
	\end{center}
	
	Suppose given triangles
	\[
	\begin{gathered}
		(X,Y,Z',u,j,\cdot),\\
		(Y,Z,X',v,\cdot,i),\\
		(X,Z,Y',vu,\cdot,\cdot)
	\end{gathered}
	\]
	Then there exist morphisms $f\colon Z'\to Y'$ and $g\colon Y'\to X'$ such that
	\[
	(Z',Y',X',f,g,T(j)i)
	\]
	is a triangle, and the two other faces of the octahedron with $f,g$ as edges, are commutative diagrams.
\end{enumerate}

\begin{definition}
	An additive functor $F\colon \mathcal{C}\to\mathcal{C}'$ from one triangulated category to another is called a \emph{(covariant) $\partial$-functor} if it commutes with the translation functor and takes triangles into triangles. A contravariant $\partial$-functor takes triangles into triangles with the arrows reversed and sends the translation functor into its inverse.
\end{definition}

\begin{definition}
	An additive functor $H\colon \mathcal{C}\to\mathcal{A}$ from a triangulated category to an abelian category is called a \emph{covariant cohomological functor} if whenever $(X,Y,Z,u,v,w)$ is a triangle, the long sequence
	\[
	\cdots\to H(T^iX)\to H(T^iY)\to H(T^iZ)\to H(T^{i+1}X)\to\cdots
	\]
	is exact (the morphisms being $H(T^iu)$, etc.). If $H$ is a cohomological functor, we often write $H^i(X)$ for $H(T^iX)$, $i\in\mathbb{Z}$. One defines a contravariant cohomological functor by reversing the arrows.
\end{definition}

\begin{proposition}\label{prop:1.1}
	\begin{enumerate}
		\item[a)] The composition of any two consecutive morphisms in a triangle is zero.
		\item[b)] If $\mathcal{C}$ is a triangulated category and $M$ an object of $\mathcal{C}$, then $\Hom_{\mathcal{C}}(M,\cdot)$ and $\Hom_{\mathcal{C}}(\cdot,M)$ are cohomological functors on $\mathcal{C}$.
		\item[c)] If in the situation of (TR3) $f$ and $g$ are isomorphisms, then $h$ is also an isomorphism.
	\end{enumerate}
\end{proposition}

\begin{proof}
	a) Let $(X,Y,Z,u,v,w)$ be a triangle. By (TR2) it is sufficient to show that $vu=0$, Also by (TR2), $(Y,Z,T(X),v,w,-T(u))$ is a triangle. By (TR1), $(Z,Z,0,\operatorname{id}_Z,0,0)$ is a triangle. We apply (TR3) to the maps $v\colon Y\to Z$ and $\operatorname{id}_Z\colon Z\to Z$, and conclude that there is a map $h:T(X)\rightarrow 0$ giving a morphism of triangles. It follows that $T(v)(-T(u))=0$, or, since $T$ is an automorphism, $vu=0$.
	
	b) Let $M\in \Ob(\mathcal{C})$, and let $(X,Y,Z,u,v,w)$ be a triangle. To show $\Hom_{\mathcal{C}}(M,\cdot)$ is a cohomological functor, it suffices by (TR2) to show the sequence
	\[
	\Hom_{\mathcal{C}}(M,X)\to\Hom_{\mathcal{C}}(M,Y)\to\Hom_{\mathcal{C}}(M,Z)
	\]
	is exact. By a) we know the composition is zero. Now suppose given $g\in\Hom_{\mathcal{C}}(M,Y)$ such that $vg\in \Hom_{\mathcal{C}}(M,Z)$ is zero. We apply (TR3) to the triangles $(M,M,0,\operatorname{id}_M,0,0)$ and $(X,Y,Z,u,v,w)$ and the map $g\colon M\to Y$ to conclude there exists $f\colon M\to X$ such that $uf=g$.
	
	A similar proof shows that $\Hom_{\mathcal{C}}(\cdot,M)$ is a contravariant cohomological functor.
	
	c) In the situation of (TR3) suppose that $f$ and $g$ are isomorphisms. We apply the cohomological functor $\Hom_{\mathcal{C}}(Z', \cdot)$ to the whole situation, and obtain an exact commutative diagram
	
	\[
\resizebox{.9\hsize}{!}	{	$ 
	\begin{CD}
		\Hom(Z',X) @>>> \Hom(Z',Y) @>>> \Hom(Z',Z) @>>> \Hom(Z',T(X)) @>>> \Hom(Z',T(Y)) \\
		@V{f_*}VV @V{g_*}VV @V{h_*}VV @V{T(f)_*}VV @V{T(g)_*}VV \\
		\Hom(Z',X') @>>> \Hom(Z',Y') @>>> \Hom(Z',Z') @>>> \Hom(Z',T(X')) @>>> \Hom(Z',T(Y'))
	\end{CD}
	$
	}\]
	
	where $f_* = \Hom(Z', f)$ etc. Now since $f$ and $g$ are isomorphisms in $\mathcal{C}$, it follows that $f_*, g_*, T(f)_*$, and $T(g)_*$ are isomorphisms of abelian groups. Hence by the five-lemma, $h_*$ is an isomorphism. We conclude that there exists a $\varphi \in \Hom_{\mathcal{C}}(Z',Z)$ such that $h_*(\varphi) = h\varphi$ is $\operatorname{id}_{Z'} \in \Hom(Z',Z')$.
	
	Similarly using the cohomological functor $\Hom_{\mathcal{C}}(\cdot, Z)$ we find there is a $\psi \in \Hom(Z',Z)$ such that $\psi h = \operatorname{id}_{Z'}$. It follows that $\varphi = \psi$ and $h$ is an isomorphism.
	
\end{proof}

\section{$\KK(\mathcal{A})$ is triangulated}
Let $\mathcal{A}$ be an abelian category. A \emph{complex} of objects of $\mathcal{A}$ is a collection $X^\bullet=(X^n)_{n\in\mathbb{Z}}$ of objects of $\mathcal{A}$ together with maps $d^n\colon X^n\to X^{n+1}$ such that $d^{n+1}d^n=0$ for all $n\in\mathbb{Z}$.

A morphism $f$ of complexes $X^\bullet\to Y^\bullet$ is a collection of maps $f^n\colon X^n\to Y^n$ which commute with differentials:
\[
f^{n+1}d_X^n = d_Y^n f^n
\]
for all $n$.

Two maps $f,g\colon X^\bullet\to Y^\bullet$ are \emph{homotopic} if there exists a collection of maps $k=(k^n)$, $k^n\colon X^n\to X^{n-1}$ (not necessarily commuting with $d$) such that
\[
f^n - g^n = d_Y^{n-1}k^n + k^{n+1}d_X^n
\]
for all $n$. Homotopy is an equivalence relation, and compositions of homotopic maps are homotopic.

We define $\KK(\mathcal{A})$ to be the category whose objects are complexes of objects of $\mathcal{A}$, and whose morphisms are homotopy equivalence classes of morphisms of complexes. A complex $X^\bullet$ is \emph{bounded below} if $X^n=0$ for $n\ll0$. We denote by $\KK^+(\mathcal{A})$ the full subcategory of $\KK(\mathcal{A})$ of complexes bounded below. Similarly we define $\KK^-(\mathcal{A})$ (bounded above) and $\KK^b(\mathcal{A})$ (bounded on both sides).

We now define a triangulated structure on $\KK(\mathcal{A})$ (resp.\ $\KK^+(\mathcal{A})$, etc.). Let $T$ be the left shift functor with sign change:
\[
T(X^\bullet)^p = X^{p+1},\qquad d_{T(X)} = -d_X.
\]
We often write $X^\bullet[1]$ instead of $T(X^\bullet)$, and $X^\bullet[n]$ instead of $T^n(X^\bullet)$. If $u\colon X^\bullet\to Y^\bullet$ is any morphism, consider its \emph{mapping cone} $Z^\bullet$ of $u$, defined as the complex
\[
Z^\bullet = T(X^\bullet)\oplus Y^\bullet
\]
with differential
\[
d_Z = \begin{pmatrix} T(d_X) & T(u) \\ 0 & d_Y \end{pmatrix}.
\]
There are natural morphisms
\[
v\colon Y^\bullet\to Z^\bullet,\qquad w\colon Z^\bullet\to T(X^\bullet).
\]

We define a triangle in $\KK(\mathcal{A})$ to be any sextuple isomorphic to one obtained from a morphism $u$ by this construction.

All axioms (TR1)--(TR4) are easily verified, once one notes that the mapping cone of the identity map $\operatorname{id}_{X^\bullet}$ is homotopic to $0$. Indeed, the the mapping cone is 
$T(X^\bullet)\oplus X^\bullet$ as described above, matrix
\[
k = \begin{pmatrix} 0 & 0 \\ \operatorname{id}_X & 0 \end{pmatrix}
\]
is a homotopy operator. 

\begin{definition}
	We define $H$ to be the functor from $\KK(\mathcal{A})$ to $\mathcal{A}$ which sends a complex $X^\bullet$ to its $0^\text{th}$ cohomology:
	\[
	H(X^\bullet) = \ker d^0 \big/ \operatorname{im} d^{-1}.
	\]
	This is indeed a functor, since homotopic maps induce the same map on cohomology. We write $H^i = H\circ T^i$ for any $i\in\mathbb{Z}$.
\end{definition}

Observe that $H$ is a cohomological functor from $\KK(\mathcal{A})$ to $\mathcal{A}$. Indeed, it suffices to check the long exact sequence for triangles coming from mapping cones, which is straightforward.

\section{Localization of categories}

\begin{definition}
Let $\mathcal{C}$ be a category. A collection $S$ of morphisms of $\mathcal{C}$ is called a \emph{multiplicative system} if it satisfies the following axioms (FR1)--(FR3):
\begin{enumerate}
\item[(FR1)] If $f,g\in S$ and the composite $fg$ exists, then $fg\in S$. For any $X\in\operatorname{Ob}\mathcal{C}$, $\operatorname{id}_X\in S$.

\item[(FR2)] Any diagram
\[
X\xrightarrow{u} Y \xleftarrow{s} Z,\quad s\in S
\]
can be completed to a commutative diagram
\[
\begin{CD}
W @>v>> Z\\
@VtVV @VsVV\\
X @>u>> Y
\end{CD}
\]
with $t\in S$. The analogous statement holds with all arrows reversed.

\item[(FR3)] Let $f,g\colon X\to Y$ be morphisms in $\mathcal{C}$. The following are equivalent:
\begin{enumerate}
\item[(i)] There exists $s\colon Y\to Y'$ in $S$ such that $sf = sg$;
\item[(ii)] There exists $t\colon X'\to X$ in $S$ such that $ft = gt$.
\end{enumerate}
\end{enumerate}
\end{definition}

\begin{definition}
Let $\mathcal{C}$ be a category and $S$ a collection of morphisms in $\mathcal{C}$. The \emph{localization of $\mathcal{C}$ with respect to $S$} is a category $\mathcal{C}_S$ together with a functor $Q\colon\mathcal{C}\to\mathcal{C}_S$ such that:
\begin{enumerate}
\item[(a)] $Q(s)$ is an isomorphism for every $s\in S$;
\item[(b)] Any functor $F\colon\mathcal{C}\to\mathcal{D}$ sending each $s\in S$ to an isomorphism factors uniquely through $Q$.
\end{enumerate}
\end{definition}
\textbf{Remark.}
	One can show that such a localization exists without 
	hypotheses on $S$, but we will not need this result. 

\begin{proposition}\label{prop:1.3.1}
Let $\mathcal{C}$ be a category and $S$ a multiplicative system in $\mathcal{C}$. The localization $\mathcal{C}_S$ may be constructed as follows:
$\operatorname{Ob}\mathcal{C}_S = \operatorname{Ob}\mathcal{C}$, and for all $X,Y\in\operatorname{Ob}\mathcal{C}$,
\[
\Hom_{\mathcal{C}_S}(X,Y) = \varinjlim_{I_X} \Hom_{\mathcal{C}}(X',Y),
\]
where $I_X$ is the category whose objects are morphisms $s\colon X'\to X$ in $S$, and morphisms are commutative diagrams:
\[
\begin{tikzcd}
	X'' \arrow[dr, "s2"] \arrow[r, "f"] & X' \arrow[d, "s1"] \\
	& X
\end{tikzcd}
\]

Furthermore, if $\mathcal{C}$ is an additive category,, then $\mathcal{C}_S$ is also additive.
\end{proposition}

\begin{proof}
First observe, using (FR1), (FR2), and (FR3) that the category \(I_X\) satisfies the axioms L1, L2, L3 of [GT, Ch. I, §1], and hence behaves as well as an inductive system for taking limits. Thus a morphism of \(X\) to \(Y\) in \(C_S\) is represented by a diagram
\[
\begin{tikzcd}
	& X' \arrow[ld, "s"'] \arrow[rd, "a"] & \\
	X & & Y
\end{tikzcd}
\]
with \(s \in S\). This diagram defines the same morphism as another one with \(t \in S\)
\[
\begin{tikzcd}
	& X'' \arrow[ld, "t"'] \arrow[rd, "b"] & \\
	X & & Y
\end{tikzcd}
\]
if and only if there is a morphism \(u: X''' \longrightarrow X\) in \(S\) and morphisms \(f: X''' \longrightarrow X'\) and \(g: X''' \longrightarrow X''\) such that \(sf = u = tg\) and \(af = bg\).

To compose morphisms
\[
\begin{tikzcd}
	& X' \arrow[ld, "s"'] \arrow[rd, "a"] & \\
	X & & Y
\end{tikzcd}
\quad \text{and} \quad
\begin{tikzcd}
	& Y' \arrow[ld, "t"'] \arrow[rd, "b"] & \\
	Y & & Z
\end{tikzcd}
\]
we use (FR2) to find a commutative diagram
\[
\begin{tikzcd}
	& & X'' \arrow[ld, "t'"'] \arrow[rd, "c"] & & \\
	& X' \arrow[ld, "s"'] \arrow[rd, "a"] & & Y' \arrow[ld, "t"'] \arrow[rd, "b"] & \\
	X & & Y & & Z
\end{tikzcd}
\]
with \(t' \in S\), and then take \(X''\), \(st'\), \(bc\) to be the composition. One verifies easily that the resulting morphism of \(X\) to \(Z\) is independent of the representatives of the morphisms of \(X\) to \(Y\) and \(Y\) to \(Z\) chosen, and is also independent of the commutative diagram chosen.

One can also verify easily that the functor \(Q: C \longrightarrow C_S\) has the properties required and that \(C_S\) is additive if \(C\) is (again using L1, L2, L3 to show that the \(\varinjlim\) is a group).

\end{proof}

\begin{definition}
Let $\mathcal{C}$ be a triangulated category and $S$ a multiplicative system in $\mathcal{C}$. We say $S$ is \emph{compatible with the triangulation} if:
\begin{enumerate}
\item[(FR4)] $s\in S \implies T(s)\in S$, where $T$ is the translation functor;
\item[(FR5)] Axiom (TR3) holds with the extra condition: if $f,g\in S$ are the given morphisms of triangles, then  $h\in S$.
\end{enumerate}
\end{definition}

\begin{proposition}\label{prop:1.3.2}
If $\mathcal{C}$ is triangulated and $S$ a multiplicative system compatible with triangulation, then $\mathcal{C}_S$ has a unique structure of triangulated category such 
that $Q$ is a $\partial$-functor, and $Q$ has the universal property b) 
above for $\partial$-functors into triangulated categories. 
\end{proposition}

\begin{proof}
	Left to the reader. It helps to observe that one can also calculate $\Hom_{C_S}(X,Y)$ as
	\[
	\varinjlim_{J_Y} \Hom_C(X,Y')
	\]
	where $J_Y$ is the category whose objects are morphisms $s: Y \longrightarrow Y'$ in $S$, and whose maps are commutative diagrams
	\[
	\begin{tikzcd}
		& Y \arrow[ld, "s_1"'] \arrow[rd, "s_2"] & \\
		Y' \arrow[rr, "f"] & & Y''
	\end{tikzcd}
	.
	\]
\end{proof}

\begin{proposition}\label{prop:1.3.3}
Let $\mathcal{C}$ be a category, $S$ a multiplicative system in $\mathcal{C}$, and $\mathcal{D}\subseteq\mathcal{C}$ a full subcategory (i.e. $X,Y\in \Ob D$ implies $\Hom_C(X,Y)=\Hom_D(X,Y)$) such that $S\cap\mathcal{D}$ is a multiplicative system in $\mathcal{D}$. Assume furthermore 
that one of the following two conditions holds:
\begin{enumerate}
\item[(i)] For every $s\colon X'\to X$ in $S$ with $X\in\operatorname{Ob}\mathcal{D}$, there exists $f\colon X''\to X'$ with $X''\in\operatorname{Ob}\mathcal{D}$ and $sf\in S$;
\item[(ii)] The same with all arrows reversed.
\end{enumerate}
Then the natural functor
\[
\mathcal{D}_{S\cap\mathcal{D}} \to \mathcal{C}_S
\]
is fully faithful, i.e. $\mathcal{D}_{S\cap\mathcal{D}}$ can be identified with a full subcategory of $\mathcal{C}_S$.
\end{proposition}

\begin{proposition}\label{prop:1.3.4}
Let $\mathcal{C}$ be a category, $S$ a multiplicative system, $Q\colon\mathcal{C}\to\mathcal{C}_S$ the localization functor. Let $\mathcal{D}$ be any category, and $F,G\colon\mathcal{C}_S\to\mathcal{D}$ functors. Then the natural restriction map
\[
\alpha\colon \Hom(F,G) \to \Hom(FQ,GQ)
\]
between functor morphism sets is bijective.
\end{proposition}

\begin{proof}
To give a morphism of functors \(F \longrightarrow G\) means to give for each \(X \in \operatorname{Ob} C_S\), a morphism \(F(X) \longrightarrow G(X)\), such that if \(X \longrightarrow Y\) is a morphism, then
\[
\begin{tikzcd}
	F(X) \arrow[r] \arrow[d] & F(Y) \arrow[d] \\
	G(X) \arrow[r] & G(Y)
\end{tikzcd}
\]
is a commutative diagram. Thus, since \(\operatorname{Ob} C = \operatorname{Ob} C_S\), the map \(\alpha\) is injective. To show \(\alpha\) surjective, suppose given a morphism \(FQ \longrightarrow GQ\). Then we have a morphism \(F(X) \longrightarrow G(X)\) for each \(X \in \operatorname{Ob} C = \operatorname{Ob} C_S\), and commutative diagrams for morphisms \(X \longrightarrow Y\) in \(C\). A morphism in \(C_S\) is represented by a diagram
\[
\begin{tikzcd}
	& X' \arrow[ld, "s"'] \arrow[rd, "f"] & \\
	X & & Y
\end{tikzcd}
\]
of morphisms in \(C\), with \(s \in S\). But for \(s \in S\), \(F(s)\) and \(G(s)\) are isomorphisms, so we get the required commutative diagram.

\end{proof}

\section{Quasi-isomorphisms and the derived category}

Let $\mathcal{A}$ be an abelian category, and let $\KK(\mathcal{A})$ be the triangulated category of complexes up to homotopy introduced in \S2. A morphism $f\colon X^\bullet\to Y^\bullet$ in $\KK(\mathcal{A})$ is called a \emph{quasi-isomorphism} if it induces an isomorphism on all cohomology groups. Denote by $\operatorname{Qis}$ the collection of all quasi-isomorphisms in $\KK(\mathcal{A})$.

\begin{proposition}
	$\operatorname{Qis}$
is a multiplicative system in $\KK(\mathcal{A})$. 

\end{proposition}
\begin{proof}

This is a consequence of the following more general proposition
\end{proof}
\begin{proposition}\label{prop:1.4.2}
Let $\mathcal{C}$ be a triangulated category, $\mathcal{A}$ an abelian category, and $H\colon\mathcal{C}\to\mathcal{A}$ a cohomological functor. Let $S$ be the class of morphisms $s\in\mathcal{C}$ such that $H(T^i(s))$ is an isomorphism for all $i\in\mathbb{Z}$. Then $S$ is a multiplicative system in $\mathcal{C}$ and is compatible with the triangulation.
\end{proposition}

\begin{proof}
We verify axioms (FR1)--(FR5). Axioms (FR1) and (FR4) are trivial. Axiom (FR5) follows from the long exact sequence of a cohomological functor and the five-lemma.

To prove (FR2), let a diagram is given:
\[
X\xrightarrow{u} Y \xleftarrow{s} Z
\]
with $s\in S$, Complete \(s\) to a triangle \((Z,Y,N,s,f,g)\). Complete \(fu\) to a triangle \((W,X,N,t,fu,h)\). Then \((u, \mathrm{id}_N)\) is a map of two sides of the second triangle into the first, so there is a map \(v: W \longrightarrow Z\) giving a morphism of triangles.
\[
\begin{tikzcd}
	W \arrow[rr, "v"] \arrow[dd, "t"] & & Z \arrow[dd, "s"]  & \\
	& N \arrow[ul, "h"] \arrow[rr, "\mathrm{id}_N\quad\quad"] & & N \arrow[ul, "g"'] \\
	X \arrow[rr, "u"] \arrow[ur, "fu"'] & & Y \arrow[ru, "f"] &
\end{tikzcd}
\]
Now \(sv = ut\), so it remains to prove \(t \in S\). Indeed, since \(s \in S\), we have \(H(T^i(N)) = 0\) for all \(i \in \mathbb{Z}\) by the long exact sequence of the first triangle. Applying this to the long exact sequence of the second triangle, we find \(H(T^i(t))\) is an isomorphism for all \(i \in \mathbb{Z}\).

The opposed statement of (FR2) is proved similarly.

To prove (FR3), we consider the morphism \(f-g\), and reduce to showing the following two properties equivalent (where \(f: X \longrightarrow Y\) is a morphism):

\begin{enumerate}
\item  There exists an $s\colon Y\to Y'\in S$ such that $ sf=0$
\item  There exists an $t\colon X'\to X\in S$ such that $ ft=0$
\end{enumerate}
Suppose (i) holds.
\[
\begin{tikzcd}[row sep=2em, column sep=2.5em]
	X' \arrow[d, "t"'] & Z \arrow[l, "w"'] \arrow[d, "v"] \\
	X \arrow[r, "f"'] \arrow[ru, "g"]  & Y \arrow[r, "s"']  & Y' \arrow[lu, "u"']
\end{tikzcd}
\]
By (TR1) and (TR2) we can find a triangle \((Z,Y,Y',v,s,u)\) for suitable \(Z\). Now \(sf = 0\), so by Proposition 1.1 b), there is a map \(g: X \longrightarrow Z\) such that \(f = vg\). Again by (TR1) and (TR2) we can find a triangle \((X',X,Z,t,g,w)\) for suitable \(X'\). By the same Proposition applied to this second triangle, the existence of \(v\) implies that \(ft = 0\). We need only show that \(t \in S\). Since \(s \in S\), \(H(T^i(Z)) = 0\) for all \(i \in \mathbb{Z}\), by the long exact sequence of cohomology. In turn, this implies that \(t \in S\).

The implication (ii)\(\implies\)(i) is analogous.
\end{proof}

\begin{definition}
The \emph{derived category} of $\mathcal{A}$ is
\[
\DD(\mathcal{A}) := \KK(\mathcal{A})_{\operatorname{Qis}}.
\]
Similarly define
\[
\DD^+(\mathcal{A})=\KK^+(\mathcal{A})_{\operatorname{Qis}},\quad
\DD^-(\mathcal{A})=\KK^-(\mathcal{A})_{\operatorname{Qis}},\quad
\DD^b(\mathcal{A})=\KK^b(\mathcal{A})_{\operatorname{Qis}}.
\]
By Proposition 1.3.3, these are full subcategories of $\DD(\mathcal{A})$, and
\[
\DD^+(\mathcal{A})\cap \DD^-(\mathcal{A}) = \DD^b(\mathcal{A}).
\]
\end{definition}

\begin{definition}
Let $\mathcal{A}$ be abelian, and $\mathcal{A}'\subset\mathcal{A}$ a \emph{thick} full abelian subcategory (closed under extensions in $\mathcal{A}$). Define $\KK_{\mathcal{A}'}(\mathcal{A})$ to be the full subcategory of $\KK(\mathcal{A})$ consisting of complexes $X^\bullet$ whose cohomology objects $H^i(X^\bullet)$ lie in $\mathcal{A}'$. Since $\mathcal{A}'$ is thick, $\KK_{\mathcal{A}'}(\mathcal{A})$ is a triangulated subcategory of $\KK(\mathcal{A})$.

Define
\[
\DD_{\mathcal{A}'}(\mathcal{A}) := \KK_{\mathcal{A}'}(\mathcal{A})_{\operatorname{Qis}}.
\]
By Proposition 1.3.3, $\DD_{\mathcal{A}'}(\mathcal{A})$ is the full subcategory of $\DD(\mathcal{A})$ of complexes with all cohomology in $\mathcal{A}'$. One defines similarly $\KK_{\mathcal{A}'}^+(\mathcal{A}), \DD_{\mathcal{A}'}^+(\mathcal{A})$, etc., for bounded-below complexes.
\end{definition}

\textbf{Example.} To help understand the category $\DD(\mathcal{A})$, let us ask: when does a morphism of complexes $f\colon X^\to Y$ give the zero map in $\DD(\mathcal{A})$? The condition is:

$(*)$ There exists an $s\colon Y\to Y'$ in $\operatorname{Qis}$ such that $sf$ is homotopic to zero (or, equivalently, there exists a $t\colon X'\to X$ in $\operatorname{Qis}$ such that $ft$ is homotopic to zero).

\begin{enumerate}
\item[1.] Of course, if $f\sim 0$ ($f$ homotopic to zero), then $f$ satisfies $(*)$. The converse is false. For example, take X to be the complex
\[
0\to\mathbb{Z}\xrightarrow{2}\mathbb{Z}\to\mathbb{Z}/2\mathbb{Z}\to 0,
\]
and $f$ to be the identity $\operatorname{id}_{X}\colon X\to X$. Let $g\colon X\to 0$ be the zero map. Then $g\in\operatorname{Qis}$, and $gf=0$, but $f$ is not homotopic to zero, as one sees easily.

\item[2.] If $f$ satisfies $(*)$, then $f$ induces the zero map on cohomology, but the converse is false. For example take $f\colon X\to Y$ as follows:
\[
\begin{tikzcd}
\cdots \arrow[r] & 0 \arrow[r] \arrow[d] & \mathbb{Z} \arrow[r, "2"] \arrow[d, "1"] & \mathbb{Z} \arrow[r] \arrow[d,"2"] & 0 \arrow[r] \arrow[d] & \cdots \\
\cdots \arrow[r] & 0 \arrow[r] & \mathbb{Z} \arrow[r, "1"] & \mathbb{Z}/3\mathbb{Z} \arrow[r] & 0 \arrow[r] & \cdots
\end{tikzcd}
\]
Now $f$ induces the zero map on cohomology, but there does not exist $t\colon X'\to X$ in $\operatorname{Qis}$ such that $ft\sim 0$. (The reader can supply the proof as follows: take a cycle $x\in X'$ such that $t(x)$ generates the single cohomology group $\mathbb{Z}/2\mathbb{Z}$ of $X$. If $k$ is a homotopy operator for $ft$, show that $2k(x)=1$, which is impossible.)
\end{enumerate}

So for two maps $f,g\colon X\to Y$ of complexes, we see that the following implications are all strict:
\[
\begin{aligned}
f=g
&\;\Longrightarrow\; f\text{ homotopic to }g \\
&\;\Longrightarrow\; f\text{ and }g\text{ give the same morphism in }\DD(\mathcal{A}) \\
&\;\Longrightarrow\; f\text{ and }g\text{ give the same map on cohomology}.
\end{aligned}
\]

\begin{proposition}\label{prop:1.4.3}
The functor $\mathcal{A}\to\DD(\mathcal{A})$ which sends each object $X$ of $\mathcal{A}$ into the complex consisting of $X$ in degree $0$, and $0$ elsewhere, gives an equivalence of the category $\mathcal{A}$ with the full subcategory of $\DD(\mathcal{A})$ consisting of those complexes $X^\bullet$ such that $H^i(X^\bullet)=0$ for $i\neq 0$.
\end{proposition}

We now prove three lemmas, which give an alternative description of $\DD^+(\mathcal{A})$ when $\mathcal{A}$ has enough injectives.

\begin{lemma}\label{lem:1.4.4}
Let $\mathcal{A}$ be abelian, $f\colon Z^\bullet\to I^\bullet$ a morphism of complexes. Assume:
\begin{enumerate}
\item[(1)] $Z^\bullet$ is acyclic;
\item[(2)] Each $I^p$ is injective in $\mathcal{A}$;
\item[(3)] $I^\bullet$ is bounded below.
\end{enumerate}
Then $f$ is homotopic to zero.
\end{lemma}
\begin{proof}
	Well known (and easy).
\end{proof}
\begin{lemma}\label{lem:1.4.5}
Let $\mathcal{A}$ be abelian, $s\colon I^\bullet\to Y^\bullet$ a morphism of complexes. Assume:
\begin{enumerate}
\item[(1)] $s$ induces an isomorphism on cohomology;
\item[(2)] Each $I^p$ is injective;
\item[(3)] $I^\bullet$ is bounded below.
\end{enumerate}
Then $s$ admits a homotopy inverse.
\end{lemma}

\begin{proof}
Suppose given $s\colon I^\bullet\to Y^\bullet$ as above. Let $Z^\bullet = T(I^\bullet)\oplus Y^\bullet$ be the mapping cone of $s$. Then $Z^\bullet$ is acyclic, and so the triangular morphism $v\colon Z^\bullet\to T(I^\bullet)$ satisfies the conditions of Lemma 1.4.4, and so is homotopic to zero. Let us call the homotopy operator
\[
(k,t)\colon T(I^\bullet)\oplus Y^\bullet \longrightarrow I^\bullet.
\]
Then we have the equation
\[
v = (\operatorname{id}_{I^\bullet},0) = (k,t)d_Z + d_{I^\bullet}(k,t).
\]
Separating the components, we find
\[
\operatorname{id}_{T(I^\bullet)} = dk + kd + ts
\]
and
\[
dt - td = 0.
\]
Thus $t\colon Y^\bullet\to I^\bullet$ is a morphism of complexes, and $\operatorname{id}_{I^\bullet}$ is homotopic to $ts$, so $t$ is a homotopy inverse of $s$.
\end{proof}

\begin{lemma}\label{lem:1.4.6}
Let $\mathcal{A}$ be an abelian category.
\begin{enumerate}
\item[1)] Let $P\subseteq\operatorname{Ob}\mathcal{A}$ and assume:
\begin{enumerate}
\item[(i)] Every object of $\mathcal{A}$ admits an injection into an element of $P$.
\end{enumerate}
Then every complex $X^\bullet\in\KK^+(\mathcal{A})$ admits a quasi-isomorphism into a bounded-below complex $I^\bullet$ of objects of $P$.

\item[2)] Assume further that $P$ satisfies:
\begin{enumerate}
\item[(ii)] If $0\to X\to Y\to Z\to 0$ is exact and $X\in P$, then $Y\in P\iff Z\in P$;
\item[(iii)] There exists a positive integer $n$ such that for any exact sequence
\[
X^0\to X^1\to\cdots\to X^{n-1}\to X^n\to 0,
\]
if $X^0,\dots,X^{n-1}\in P$ then $X^n\in P$.
\end{enumerate}
Then every $X^\bullet\in\KK(\mathcal{A})$ admits a quasi-isomorphism into a complex $I^\bullet$ of objects of $P$.

\item[3)] Let $\mathcal{A}'$ be a thick subcategory of $\mathcal{A}$, and suppose $\mathcal{A}'$ has enough $\mathcal{A}$-injectives. Then every $X^\bullet\in\KK_{\mathcal{A}'}^+(\mathcal{A})$ admits a quasi-isomorphism into a bounded-below complex $I^\bullet$ of $\mathcal{A}$-injective objects of $\mathcal{A}'$.
\end{enumerate}
\end{lemma}

\begin{proof}[Proof of 1)]
We may assume $X^p=0$ for $p<0$. Embed $X^0\hookrightarrow I^0$ with $I^0\in P$. Having defined $I^0,I^1,\dots,I^p$, choose $I^{p+1}\in P$ containing
\[
I^p\big/\operatorname{im}I^{p-1}\;\oplus\;X^{p+1},
\]
and define differentials $I^p\to I^{p+1}$ and morphisms $X^{p+1}\to I^{p+1}$ canonically. One verifies $X^\bullet\to I^\bullet$ is a quasi-isomorphism, Note that in this construction all the maps $X^p\to I^p$ is injective.
\end{proof}

\begin{proof}[Proof of 2)]
Let $X^\bullet$ be any complex. For a fixed integer $i_0$, by 1), we can find a quasi- 
isomorphism of the truncated complex 
\[
0\to 0\to X^{i_0}\to X^{i_0+1}\to\cdots
\]
 into a complex $I^\bullet$ of objects of $P$, with each $X^i\to I^i$ injective. Define $X_0^\bullet$ by
\[
\cdots\to X^{i_0-2}\to X^{i_0-1}\to I^{i_0}\to I^{i_0+1}\to\cdots.
\]
Then $X^\bullet\to X_0^\bullet$ is a quasi-isomorphism, $X_0^i\in P$ for $i\ge i_0$, and each $X^i\to X_0^i$ is injective.

Suppose given a complex $X_1^\bullet$ with $X_1^i\in P$ for $i\ge i_1$, and let $i_2<i_1$. Then we will construct a quasi-isomorphism $X_1^\bullet\to X_2^\bullet$ such that $X_2^i\in P$ for $i\ge i_2$, and $X_1^i=X_2^i$ for $i\ge i_1+n$. (Here $n$ is the integer of condition (iii) above.) Indeed, by the first step above, we can find a quasi-isomorphism $X_1^\bullet\to X'^\bullet$ such that $X'^i\in P$ for $i\ge i_2$, and each $X_1^i\to X'^i$ is injective. Let $Y^i=\operatorname{coker}(X_1^i\to X'^i)$. Then $Y^\bullet$ is an acyclic complex, and $Y^i\in P$ for $i\ge i_1$, by condition (ii) above. Hence $B^i(Y^\bullet)\in P$ for $i\ge i_1+n$, by condition (iii). Now define $X_2^\bullet$ by
\[
X_2^i=
\begin{cases}
X'^i & \text{for } i < i_1+n,\\[2pt]
B^i(X'^\bullet) \oplus_{X_1^{i-1}} X_1^i & \text{for } i = i_1+n,\\[2pt]
X_1^i & \text{for } i > i_1+n.
\end{cases}
\]
One sees easily that $X_1^\bullet\to X_2^\bullet$ is a quasi-isomorphism. It follows from (ii) and the exact sequence
\[
0 \longrightarrow X_1^i \longrightarrow B^i(X'^\bullet) \oplus_{X_1^{i-1}} X_1^i \longrightarrow B^i(Y^\bullet) \longrightarrow 0
\]
that the middle term is in $P$, for $i\ge i_1+n$, so $X_2^\bullet$ is as required.

Now, given a complex $X^\bullet\in\KK(\mathcal{A})$, choose a sequence of integers $i_0>i_1>i_2>\cdots$ tending to $-\infty$. Choose $X_0^\bullet$ for $i_0$ as in the first step, and choose $X_1^\bullet,X_2^\bullet,\dots$ for $i_1,i_2,\dots$ successively as in the second step. Then we have quasi-isomorphisms
\[
X^\bullet \longrightarrow X_0^\bullet \longrightarrow X_1^\bullet \longrightarrow X_2^\bullet \longrightarrow \cdots,
\]
and for each $i$, the sequence $X^i\to X_0^i\to X_1^i\to\cdots$ is eventually constant, and eventually in $P$. Hence $I^\bullet = \varinjlim X_r^\bullet$ is the required complex of objects of $P$.
\end{proof}

\begin{proof}[Proof of 3)]
We may assume $X^i=0$ for $i<0$. Embed $H^0(X^\bullet)$ in $I^0$, an $\mathcal{A}$-injective of $\mathcal{A}'$, which is possible since $H^0(X^\bullet)\in\operatorname{Ob}\mathcal{A}'$. Extend this to a map $f^0\colon X^0\to I^0$, which is possible since $I^0$ is $\mathcal{A}$-injective.

Having defined $I^0,I^1,\dots,I^p$ and $f^i\colon X^i\to I^i$ for $i=0,\dots,p$, choose $I^{p+1}$ to be an $\mathcal{A}$-injective of $\mathcal{A}'$ containing
\[
I^p\big/\operatorname{im}I^{p-1} \oplus_{X^p} Z^{p+1}(X^\bullet). \tag{*}
\]

We must check that this latter is in $\mathcal{A}'$. Indeed, $\mathcal{A}'$ is a thick subcategory, so it is sufficient to note that $I^p/\operatorname{im}I^{p-1}\in\mathcal{A}'$ (one shows by induction that $B^i(I^\bullet)$ and $Z^i(I^\bullet)$ are in $\mathcal{A}'$ for all $i$), and that the quotient of $(*)$ by $I^p/\operatorname{im}I^{p-1}$ is $H^{p+1}(X^\bullet)$, which is in $\mathcal{A}'$ by hypothesis. Extend the natural map $Z^{p+1}(X^\bullet)\to I^{p+1}$ to a map $f^{p+1}\colon X^{p+1}\to I^{p+1}$. One checks easily that the resulting map $f\colon X^\bullet\to I^\bullet$ is a quasi-isomorphism, as required.
\end{proof}

\begin{proposition}\label{prop:1.4.7}
Let $\mathcal{A}$ be abelian, and let $\mathcal{I}$ be the additive subcategory of injective objects of $\mathcal{A}$. The natural functor
\[
\alpha\colon \KK^+(\mathcal{I})\to \DD^+(\mathcal{A})
\]
is fully faithful. (Note that the results of section 3 carry over to additive subcategories of abelian categories.) Furthermore, if $\mathcal{A}$ has enough injectives (i.e., if every object of $\mathcal{A}$ admits an injection into an injective object), then $\alpha$ is an equivalence of categories.
\end{proposition}

\begin{proof}
We note that $\operatorname{Qis}\cap\KK^+(\mathcal{I})$ is a multiplicative system in $\KK^+(\mathcal{I})$, by Proposition 1.4.2, and we observe by Lemma 1.4.5 that condition (ii) of Proposition 1.3.3 is satisfied for $\KK^+(\mathcal{I})\subseteq\KK^+(\mathcal{A})$ and $\operatorname{Qis}$. Hence the natural functor
\[
\DD^+(\mathcal{I}) \longrightarrow \DD^+(\mathcal{A})
\]
is fully faithful. But on the other hand, Lemma 1.4.5 shows also that every quasi-isomorphism in $\KK^+(\mathcal{I})$ is an isomorphism, hence $\KK^+(\mathcal{I}) = \DD^+(\mathcal{I})$.

Now if $\mathcal{A}$ has enough injectives, applying Lemma 1.4.6 in the case $\mathcal{A}=\mathcal{B}$ and $P = {}$the injective objects, we see that every object of $\DD^+(\mathcal{A})$ is isomorphic to an object in $\KK^+(\mathcal{I})$, so $\alpha$ is an equivalence of categories.
\end{proof}

\begin{proposition}\label{prop:1.4.8}
Let $\mathcal{A}$ be abelian, $\mathcal{A}'\subseteq\mathcal{A}$ a thick abelian subcategory. Assume $\mathcal{A}'$ has enough $\mathcal{A}$-injectives, i.e~ every object of $A'$ can be injected into an 
$A$-injective object of $A'$. Then the natural functor
\[
\DD^+(\mathcal{A}') \to \DD_{\mathcal{A}'}^+(\mathcal{A})
\]
is an equivalence of categories.
\end{proposition}

\begin{proof}
We apply Proposition 1.3.3 to the inclusion $\KK^+(\mathcal{A}')\hookrightarrow\KK^+(\mathcal{A})$. Clearly $\operatorname{Qis}$ is a multiplicative system in each. If $X^\bullet\to Y^\bullet$ is a quasi-isomorphism with $X^\bullet\in\KK^+(\mathcal{A}')$, then $Y^\bullet$ has cohomology in $\mathcal{A}'$, and so by Lemma 1.4.6 admits a quasi-isomorphism $Y^\bullet\to I^\bullet$ with $I^\bullet\in\KK^+(\mathcal{A}')$, each $I^p$ injective in $\mathcal{A}$. Hence condition (ii) is satisfied, and so the functor
\[
\DD^+(\mathcal{A}') \longrightarrow \DD^+(\mathcal{A})
\]
is fully faithful. The same Lemma 1.4.6 also shows that the image is $\DD_{\mathcal{A}'}^+(\mathcal{A})$.
\end{proof}

\textbf{Exercise.} We leave to the reader the analogous statements of the last five results in the case of projective objects of $\mathcal{A}$ and $\DD^-(\mathcal{A})$.

\section{Derived functors}

We will treat only the question of \emph{right derived covariant functors}, leaving the reader to make the obvious modifications for left derived covariant functors, and right and left derived contravariant functors.

Let $\mathcal{A},\mathcal{B}$ be abelian categories, and let $F\colon\KK(\mathcal{A})\to\KK(\mathcal{B})$ be a $\partial$-functor (cf.\ \S1). Such is the case, for example, if we are given an additive functor $F\colon\mathcal{A}\to\mathcal{B}$. It extends to $\KK(\mathcal{A})$.

In general, $F$ will not take quasi-isomorphisms into quasi-isomorphisms -- to say that it does is to say that it localizes 
and gives rise to a functor from  $\DD(\mathcal{A})\to\DD(\mathcal{B})$. That will be the 
case, for example, if F is an exact functor.

Thus we are led to ask if there is a functor from $\DD(\mathcal{A})$ to $\DD(\mathcal{B})$ which is at least close to $F$, and this gives rise to the notion of derived functor below. Before giving the definition we generalize slightly.

\begin{definition}
Let $\mathcal{A}$ be abelian, and let $\KK^*(\mathcal{A})\subseteq\KK(\mathcal{A})$ be a triangulated subcategory. By Proposition 1.4.2, $\KK^*(\mathcal{A})\cap\operatorname{Qis}$ is a multiplicative system in $\KK^*(\mathcal{A})$.

We say $\KK^*(\mathcal{A})$ is a \emph{localizing subcategory} of $\KK(\mathcal{A})$ if the natural functor
\[
\KK^*(\mathcal{A})_{\KK^*(\mathcal{A})\cap\operatorname{Qis}}
\;\to\;
\KK(\mathcal{A})_{\operatorname{Qis}} = \DD(\mathcal{A})
\]
is fully faithful. In this case we write $\DD^*(\mathcal{A})$ for the $\KK^*(\mathcal{A})_{\KK^*(\mathcal{A})\cap\operatorname{Qis}}$.
\end{definition}

\textbf{Examples.}
\begin{enumerate}
\item The intersection of any family of localizing subcategories is localizing.
\item $\KK^+(\mathcal{A}),\KK^-(\mathcal{A}),\KK^b(\mathcal{A})$ are localizing subcategories of $\KK(\mathcal{A})$ (cf.\ \S4).
\item If $\mathcal{A}'\subseteq\mathcal{A}$ is a thick subcategory, then $\KK_{\mathcal{A}'}(\mathcal{A}),\KK_{\mathcal{A}'}^+(\mathcal{A}),\KK_{\mathcal{A}'}^-(\mathcal{A}),\KK_{\mathcal{A}'}^b(\mathcal{A})$ are localizing subcategories of $\KK(\mathcal{A})$ (cf.\ \S4).
\item The complexes of finite injective dimension form a localizing subcategory $\KK^+(\mathcal{A})_{\mathrm{fid}}\subseteq\KK(\mathcal{A})$ (cf.\ Corollary 1.7.7).
\end{enumerate}

\begin{definition}
Let $\mathcal{A},\mathcal{B}$ be abelian categories, $\KK^*(\mathcal{A})\subseteq\KK(\mathcal{A})$ a localizing subcategory, and
\[
F\colon\KK^*(\mathcal{A})\to\KK(\mathcal{B})
\]
a $\partial$-functor.

Denote by $Q$ the localization functor $\KK^*(\mathcal{A})\to\DD^*(\mathcal{A})$ (resp.\ $\KK(\mathcal{B})\to\DD(\mathcal{B})$). The \emph{right derived functor} of $F$ is a  $\partial$-functor
\[
\DerR^*F\colon\DD^*(\mathcal{A})\to\DD(\mathcal{B})
\]
together with a functor morphism
\[
\xi\colon Q\circ F \;\to\; \DerR^*F\circ Q
\]
of functors $\KK^*(\mathcal{A})\to\DD(\mathcal{B})$, satisfying the following universal property:

If $G\colon\DD^*(\mathcal{A})\to\DD(\mathcal{B})$ is a $\partial$-functor and any functor morphism
\[
\zeta\colon Q\circ F \;\to\; G\circ Q,
\]
there exists a unique functor morphism
\[
\eta\colon \DerR^*F \to G
\]
such that
\[
\zeta = (\eta\circ Q)\circ \xi.
\]
\end{definition}

\textbf{Remarks.}
\begin{enumerate}
\item If $\DerR^*F$ exists, it is unique up to unique isomorphism of functors.
\item For standard localizing subcategories $\KK^+(\mathcal{A}),\KK^-(\mathcal{A}),\KK_{\mathcal{A}'}(\mathcal{A})$, we write
\[
\DerR^+F,\quad \DerR^-F,\quad \DerR_{\mathcal{A}'}F
\]
respectively; when no confusion arises, we write simply $\DerR F$.

\item We will write \(\RR^i F\) for \(H^i(\DerR F)\), and it will follow from the results below that if \(F\) comes from a left-exact functor \(F: A \longrightarrow B\), and if \(A\) has enough injectives, then these are the usual derived functors of \(F\).

\item If \(\varphi: F \longrightarrow G\) is a morphism of functors from \(K^*(A)\) to \(K(B)\), and if \(\DerR F\) and \(\DerR G\) both exist, then there is a unique morphism of functors
\[
\DerR \varphi: \DerR F \longrightarrow \DerR G
\]
compatible with the \(\xi\)'s. This follows immediately from the definition.
\item Let $\KK^{**}(\mathcal{A})\subseteq\KK^*(\mathcal{A})$ be localizing subcategories, if $F\colon\KK^*(\mathcal{A})\to\KK(\mathcal{B})$ is a $\partial$-functor. and if $\DerR^*F$ and $\DerR^{**}(F|_{\KK^{**}(\mathcal{A})})$ exist, there is a natural functor morphism
\[
\DerR^{**}\big(F|_{\KK^{**}(\mathcal{A})}\big)
\;\to\;
\DerR^*F\big|_{\DD^{**}(\mathcal{A})}.
\]
We do not know if this is an isomorphism in general, but it holds in all our intended applications (cf.\ Corollary 1.5.3).
\end{enumerate}

\begin{theorem}[Existence of Derived Functors]\label{thm:1.5.1}
Let $\mathcal{A},\mathcal{B},\KK^*(\mathcal{A}),F$ be as above. Suppose there exists a triangulated subcategory $\mathcal{L}\subseteq\KK^*(\mathcal{A})$ such that:
\begin{enumerate}
\item[(1)] Every object of $\KK^*(\mathcal{A})$ admits a quasi-isomorphism into some object of $\mathcal{L}$;
\item[(2)] For every acyclic complex $I^\bullet\in\operatorname{Ob}\mathcal{L}$ (i.e.\ $H^i(I^\bullet)=0$ for all $i$), the complex $F(I^\bullet)$ is also acyclic.
\end{enumerate}
Then the right derived functor $(\DerR^*F,\xi)$ exists. Furthermore, for any $I^\bullet\in\operatorname{Ob}\mathcal{L}$, the map
\[
\xi(I^\bullet)\colon Q\circ F(I^\bullet) \to \DerR^*F\circ Q(I^\bullet)
\]
is an isomorphism in $\DD(\mathcal{B})$.
\end{theorem}

\begin{proof}
First, the restriction $F|_{\mathcal{L}}$ sends quasi-isomorphisms to quasi-isomorphisms. Indeed, let $s\colon I_1^\bullet\to I_2^\bullet$ be a quasi-isomorphism in $\mathcal{L}$; complete $s$ to a triangle in $\KK^*(\mathcal{A})$, and let $J^\bullet$ be
the third side of that triangle. Then $J^\bullet$  is acyclic, so $F(J^\bullet)$ is acyclic. Hence $F(s)$ is a quasi-isomorphism.

Thus $F$ passes to the quotient to give a functor 
\[
\overline{F}\colon\mathcal{L}_{\operatorname{Qis}} \to \DD(\mathcal{B})
\]
satisfying $\overline{F}\circ Q = Q\circ F$ on $\mathcal{L}$ (we denote as usual by $Q$
the morphism from a category to its localization).

Second, by the condition of Proposition 1.3.3, (ii) are satisfied for $\mathcal{L},\KK^*(\mathcal{A}),\operatorname{Qis}$, and so the natural functor
\[
T\colon\mathcal{L}_{\operatorname{Qis}} \to \DD^*(\mathcal{A})
\]
is an equivalence of categories, using 1) above. Let $U$ be a quasi-inverse of $T$, i.e. a functor $U\colon\DD^*(\mathcal{A})\to\mathcal{L}_{\operatorname{Qis}}$ with functorial isomorphisms
\[
\alpha\colon \operatorname{id}_{\mathcal{L}_{\operatorname{Qis}}} \to U\circ T,\qquad
\beta\colon \operatorname{id}_{\DD^*(\mathcal{A})} \to T\circ U.
\]

Define
\[
\DerR^*F := \overline{F}\circ U.
\]

We now define the functor morphism
\[
\xi\colon Q\circ F \to \DerR^*F\circ Q = \overline{F}\circ U\circ Q
\]
as follows. Given $X^\bullet\in\operatorname{Ob}\KK^*(\mathcal{A})$, choose $I^\bullet\in\operatorname{Ob}\mathcal{L}$ such that $Q(I^\bullet)\cong U\circ Q(X^\bullet)$ in $\DD^*(\mathcal{A})$.

We have an isomorphism in $\DD^*(\mathcal{A})$,
\[
\beta\big(Q(X^\bullet)\big)\colon Q(X^\bullet) \stackrel{\sim}{\longrightarrow}
T\circ U\big(Q(X^\bullet)\big) = T\big(Q(I^\bullet)\big).
\]
This isomorphism may be represented by a diagram in $\KK^*(\mathcal{A})$
\[
X^\bullet \xrightarrow{t} Y^\bullet \xleftarrow{s} I^\bullet
\quad \quad \quad \quad (*)\]
with $s,t\in\operatorname{Qis}$ and $Y^\bullet\in\operatorname{Ob}\KK^*(\mathcal{A})$. Furthermore by hypothesis (1), we may assume $Y^\bullet\in\operatorname{Ob}\mathcal{L}$. Applying the functor $F$, we obtain a diagram in $\KK(\mathcal{B})$:
\[
F(X^\bullet) \xrightarrow{F(t)} F(Y^\bullet)\xleftarrow{F(s)}  F(I^\bullet).
\]
As observed previously, $F(s)$ is also a quasi-isomorphisms.

This induces a morphism in $\DD(\mathcal{B})$:
\[
\xi(X^\bullet)\colon Q\circ F(X^\bullet)
\to Q\circ F(I^\bullet)
= \overline{F}\circ Q(I^\bullet)
= \overline{F}\circ U\circ Q(X^\bullet)
= \DerR^*F\circ Q(X^\bullet).
\]

One can now check without difficulty that $\xi(X^\bullet)$  does not depend on 
the choice of the diagram (*) above, that $\xi$ defines a functor morphism $Q\circ F\to \DerR^*F\circ Q$, and that the pair $(\DerR^*F,\xi)$ satisfies the universal property of the right derived functor.

If $X^\bullet\in\operatorname{Ob}\mathcal{L}$, then $F(t)$ is also a quasi-isomorphism in the construction above, so $\xi(X^\bullet)$ is an isomorphism in $\DD(\mathcal{B})$, as required.
\end{proof}

\begin{proposition}\label{prop:1.5.2}
Let $\mathcal{A},\mathcal{B},\KK^*(\mathcal{A}),F$ be as above, and let $\KK^{**}(\mathcal{A})\subseteq\KK^*(\mathcal{A})$ be another localizing subcategory of $\KK(\mathcal{A})$. Suppose there exists a triangulated subcategory $\mathcal{L}\subseteq\KK^*(\mathcal{A})$ satisfying hypotheses (1),(2) of Theorem 1.5.1, and such that $\mathcal{L}\cap\KK^{**}(\mathcal{A})$ satisfies hypothesis (1) for $\KK^{**}(\mathcal{A})$.
Then  $\DerR^*F$ and $\DerR^{**}\big(F|_{\KK^{**}(\mathcal{A})}\big)$ both exist, and the natural morphism
\[
\DerR^{**}\big(F|_{\KK^{**}(\mathcal{A})}\big)
\;\to\;
\DerR^*F\big|_{\DD^{**}(\mathcal{A})}
\]
is an isomorphism.
\end{proposition}

\begin{proof}
Existence follows immediately from Theorem 1.5.1. For the isomorphism, any object of $\DD^{**}(\mathcal{A})$ is isomorphic to one coming from an object of $\mathcal{L}$, we may assume that $X'' =  Q(I^\bullet)$ for some $I^\bullet\in\Ob \mathcal{L}\cap\KK^{**}(\mathcal{A})$. The claim then follows from the final assertion of Theorem 1.5.1.
\end{proof}

\begin{corollary}\label{cor:1.5.3}
\emph{$\alpha$)} Let $\mathcal{A},\mathcal{B}$ be abelian categories, $F\colon\KK^+(\mathcal{A})\to\KK(\mathcal{B})$ a $\partial$-functor (e.g., induced by an additive functor $F_0\colon\mathcal{A}\to\mathcal{B}$). If $\mathcal{A}$ has enough injectives, then $\DerR^+F$ exists.

\emph{$\beta$)} Let $\mathcal{A},\mathcal{B}$ be abelian categories, $F\colon\mathcal{A}\to\mathcal{B}$ additive. Suppose there exists an subset $P\subseteq\operatorname{Ob}\mathcal{A}$ satisfying (i),(ii) of Lemma 1.4.6, and:
\begin{enumerate}
\item[(iv)] $F$ sends short exact sequences in $\mathcal{A}$ to short exact sequences in $\mathcal{B}$.
\end{enumerate}
Then $\DerR^+F$ exists (we also denote by $F$ its extension to a $\partial$-functor $\KK^+(\mathcal{A})\to\KK^+(\mathcal{B})$).

\emph{$\gamma$)} Let $\mathcal{A},\mathcal{B}$ be abelian categories, $F\colon\mathcal{A}\to\mathcal{B}$ additive. Assume:
\begin{enumerate}
\item[(a)] The hypotheses of $\beta$ hold;
\item[(b)] $F$ has finite cohomological dimension: there exists $n>0$ such that $\RR^iF(Y)=0$ for all $Y\in\operatorname{Ob}\mathcal{A}$ and all $i>n$.
\end{enumerate}
Then $\DerR F$ exists on all of $\DD(\mathcal{A})$, and its restriction to $\DD^+(\mathcal{A})$ coincides with $\DerR^+F$.
\end{corollary}

\textbf{Remark.} Case $\alpha$ is a special case of $\beta$: if $\mathcal{A}$ has enough injectives, the class of injective objects satisfies (i),(ii),(iv) for any additive $F$.

\begin{proof}
\emph{$\alpha$)} Let $\mathcal{L}\subseteq\KK^+(\mathcal{A})$ be the triangulated subcategory of bounded-below injective complexes. By Lemma 1.4.6(1), every object of $\KK^+(\mathcal{A})$ admits a quasi-isomorphism into an object of $\mathcal{L}$. By Lemma 1.4.5, every quasi-isomorphism in $\mathcal{L}$ is an isomorphism, so acyclic objects of $\mathcal{L}$ are zero in $\KK(\mathcal{A})$. Thus condition (2) of Theorem 1.5.1 holds for any $\partial$-functor $F$, so $\DerR^+F$ exists.

\emph{$\beta$)} Take $\mathcal{L}\subseteq\KK^+(\mathcal{A})$ to be the triangulated 
subcategory of complexes of objects of $P$ (Note $\mathcal{L}$ is a 
triangulated subcategory because $P$ is stable under direct sums 
by (ii).). Condition (1) holds of the theorem is satisfied as above. For (2), let $Z^\bullet\in\mathcal{L}$ be acyclic; using (ii) repeatedly, all kernels $\ker d_Z^p$ lie in $P$. By (iv), $F$ preserves exactness, so $F(Z^\bullet)$ is acyclic.

\emph{$\gamma$)} Let $P'$ be the collection of $F$-acyclic objects of $\mathcal{A}$ ($\RR^iF(X)=0,\forall i>0$). Then $P'$ satisfies (i),(ii),(iii) of Lemma 1.4.6. Let $\mathcal{L}\subseteq\KK(\mathcal{A})$ be complexes of objects of $P'$. By Lemma 1.4.6 and the argument for $\beta$, the hypotheses of Theorem 1.5.1 are satisfied, so $\DerR F$ exists.

By Proposition 1.5.2, the restriction of $\DerR F$ to $\DD^+(\mathcal{A})$ is isomorphic to $\DerR^+F$.
\end{proof}

\begin{proposition}\label{prop:1.5.4}
Let $\mathcal{A},\mathcal{B},\mathcal{C}$ be abelian categories, $\KK^*(\mathcal{A})\subseteq\KK(\mathcal{A})$, $\KK^\dagger(\mathcal{B})\subseteq\KK(\mathcal{B})$ localizing subcategories, and let
\[
F\colon\KK^*(\mathcal{A})\to\KK(\mathcal{B}),\qquad
G\colon\KK^\dagger(\mathcal{B})\to\KK(\mathcal{C})
\]
be $\partial$-functors.

\emph{a)} Assume $F(\KK^*(\mathcal{A}))\subseteq\KK^\dagger(\mathcal{B})$, that $\DerR^*F,\DerR^\dagger G,\DerR^*(G\circ F)$ exist, and $\DerR^*F(\DD^*(\mathcal{A}))\subseteq\DD^\dagger(\mathcal{B})$. Then there exists a unique functor morphism
\[
\zeta\colon \DerR^*(G\circ F) \to \DerR^\dagger G\circ \DerR^*F
\]
so the the diagram is commutative.
\[
\begin{tikzcd}
	Q \cdot G \cdot F \arrow[rr, "\xi_G"] \arrow[dd, "\xi_{G \cdot F}"'] & & \DerR^+ G \cdot Q \cdot F \arrow[dd, "\xi_F"] \\
	\\
	\DerR^*(G \cdot F) \cdot Q \arrow[rr, "\zeta \cdot Q"] & & \DerR^+ G \cdot \DerR^* F \cdot Q
\end{tikzcd}
\]
\emph{b)} Suppose there exist triangulated subcategories $\mathcal{L}\subseteq\KK^*(\mathcal{A})$, $\MM\subseteq\KK^\dagger(\mathcal{B})$ satisfying Theorem 1.5.1's hypotheses for $F,G$ respectively, and $F(\mathcal{L})\subseteq\MM$. Then the hypotheses of (a) hold, and the canonical morphism $\zeta$ is an isomorphism.
\end{proposition}

\begin{proof}
Straightforward
\end{proof}

\textbf{Remarks.}
\begin{enumerate}
\item If $F,G,H$ are three consecutive functors, 
then there is a commutative diagram of $\zeta$s (provided they all 
exist):
\[
\begin{tikzcd}
	\DerR(H \cdot G \cdot F)
	\arrow[rr, "\xi_{G \cdot F, H}"]
	\arrow[dd, "\zeta_{F, H \cdot G}"']
	& &
	\DerR H \cdot \DerR(G \cdot F)
	\arrow[dd, "\zeta_{F, G}"] \\
	\\
	\DerR(H \cdot G) \cdot \DerR F
	\arrow[rr]
	& &
	\DerR H \cdot \DerR G \cdot \DerR F
\end{tikzcd}
\]
\item This proposition shows the convenience of derived 
functors in the context of derived categories. What used to be 
a 
spectral sequence becomes now simply a composition of functors. 
(And of course one can recover the old spectral sequence from 
this proposition by taking cohomology and using the spectral 
sequence of a double complex.)
\end{enumerate}
\begin{corollary}
	 Left to the reader: Illustrate the Proposition in the style of Corollary 5.3.
\end{corollary}
\begin{proposition}\label{prop:1.5.6}
Let $\mathcal{A}$ be an abelian category, let $\mathcal{A}'$ be a thick abelian subcategory, let $\mathcal{B}$ be another abelian category, and let $F\colon\KK^+(\mathcal{A})\to\KK^+(\mathcal{B})$ be a $\partial$-functor. Suppose that $\DerR^+F$ and $\DerR^+\big(F|_{\mathcal{A}'}\big)$ both exist. Then there is a natural morphism
\[
\zeta\colon \DerR^+\big(F|_{\mathcal{A}'}\big) \longrightarrow \varphi\circ \DerR^+F
\]
of functors from $\DD^+(\mathcal{A}')$ to $\DD(\mathcal{B})$, where
\[
\varphi\colon\DD^+(\mathcal{A}')\longrightarrow\DD^+(\mathcal{A})
\]
is the natural functor. If furthermore $\mathcal{A}'$ has enough $\mathcal{A}$-injectives, and $\mathcal{A}$ has enough injectives, then $\zeta$ is an isomorphism.
\end{proposition}

\begin{proof}
The existence of $\zeta$ follows from the definition of the derived functor. If $\mathcal{A}'$ has enough $\mathcal{A}$-injectives, and $\mathcal{A}$ has enough injectives, then we can use $\mathcal{A}$-injectives to calculate both functors above, by Corollary 1.5.3 $\alpha$, and so $\zeta$ is an isomorphism. (Recall by Proposition 1.4.8 that $\varphi$ is an equivalence of categories in that case.)
\end{proof}

\section{Examples. $\operatorname{Ext}$ and $\DerR\Hom$}

\begin{definition}
Let $\mathcal{A}$ be an abelian category, and let $X^\bullet,Y^\bullet\in\DD(\mathcal{A})$.
Define the \emph{$i$th hyperext groups} by
\[
\operatorname{Ext}^i\big(X^\bullet,Y^\bullet\big)
= \Hom_{\DD(\mathcal{A})}\big(X^\bullet, T^i(Y^\bullet)\big).
\]
\end{definition}

\textbf{Remarks.}
\begin{enumerate}
\item If $X^\bullet,Y^\bullet\in\DD^+(\mathcal{A})$, then $\operatorname{Ext}^i$ computed in $\DD^+(\mathcal{A})$
agrees with the above, since $\DD^+(\mathcal{A})$ is a full subcategory of $\DD(\mathcal{A})$.

\item This gives in particular a definition of  $\operatorname{Ext}^i(X,Y)$ for any $X,Y\in\mathcal{A}$.
We shall see that if $\mathcal{A}$ has enough injectives, this coincides with the classical
definition of Ext groups.
\end{enumerate}

\begin{proposition}\label{prop:1.6.1}
Let
\[
0 \to X^\bullet \to Y^\bullet \to Z^\bullet \to 0
\]
be a short exact sequence of complexes over $\mathcal{A}$, and let $V^\bullet$ be another complex.
Then we have long exact sequences
\[
\cdots \to \operatorname{Ext}^i(V^\bullet,X^\bullet)
\to \operatorname{Ext}^i(V^\bullet,Y^\bullet)
\to \operatorname{Ext}^i(V^\bullet,Z^\bullet)
\to \operatorname{Ext}^{i+1}(V^\bullet,X^\bullet)
\to \cdots
\]
and
\[
\cdots \to \operatorname{Ext}^i(Z^\bullet,V^\bullet)
\to \operatorname{Ext}^i(Y^\bullet,V^\bullet)
\to \operatorname{Ext}^i(X^\bullet,V^\bullet)
\to \operatorname{Ext}^{i+1}(Z^\bullet,V^\bullet)
\to \cdots
\]
\end{proposition}

\begin{proof}
Let $W^\bullet$ be the third side of a triangle on $X^\bullet \to Y^\bullet$.
\[
\begin{tikzcd}
	& & W^\bullet \arrow[ld] \arrow[rd, dashed, "g"] & \\
	0 \arrow[r] & X^\bullet \arrow[r] & Y^\bullet \arrow[u] \arrow[r] & Z^\bullet \arrow[r] & 0
\end{tikzcd}
\]
Then by Proposition 1.1(b), there is a morphism of complexes $g\colon W^\bullet \to Z^\bullet$. Using the long exact sequence of cohomology of the short exact sequence, and of the triangle, and using the five-lemma, we see that $g$ is a quasi-isomorphism, i.e., an isomorphism in $\DD(\mathcal{A})$. Hence we may replace $Z^\bullet$ by $W^\bullet$ in the conclusion, which then follows from the same proposition.
\end{proof}

\textbf{Remark.}
It follows from the proof that any short exact sequence of complexes
\[
0 \to X^\bullet \to Y^\bullet \to Z^\bullet \to 0
\]
determines a morphism $Z^\bullet\to T(X^\bullet)$ in $\DD(\mathcal{A})$, making $X^\bullet,Y^\bullet,Z^\bullet$
into a triangle.

Now we will define a functor whose cohomology gives the  $\operatorname{Ext}$ groups.

\begin{definition}
For complexes $X^\bullet,Y^\bullet$ over $\mathcal{A}$, define the complex
$\Hom^\bullet(X^\bullet,Y^\bullet)$ by
\[
\Hom^n\big(X^\bullet,Y^\bullet\big)
= \prod_{p\in\mathbb{Z}} \Hom_{\mathcal{A}}\big(X^p,Y^{p+n}\big),
\]
with differential
\[
d^n = \prod_{p\in\mathbb{Z}} \big(d_X^{p-1} + (-1)^{n+1}d_Y^{p+n}\big).
\]

Notice under this definition the $n$-cycles of $\Hom^\bullet(X^\bullet,Y^\bullet)$ correspond bijectively
to morphisms $X^\bullet\to T^n(Y^\bullet)$ of complexes.
The $n$-boundaries correspond to morphisms homotopic to zero.
In other words
\[
H^n\big(\Hom^\bullet(X^\bullet,Y^\bullet)\big)
\cong \Hom_{\KK(\mathcal{A})}\big(X^\bullet, T^n(Y^\bullet)\big).
\]

Clearly $\Hom^\bullet$ is a bi-$\partial$-functor
\[
\Hom^\bullet\colon\KK(\mathcal{A})^\circ \times \KK(\mathcal{A}) \to \KK(\mathbf{Ab}).
\]
\end{definition}

If $\mathcal{A}$ has enough injectives, we can calculate its derived   functors.

\begin{lemma}\label{lem:1.6.2}
Let $X^\bullet\in\KK(\mathcal{A})$ be a complex, $Y^\bullet\in\KK^+(\mathcal{A})$ be a complex of injectives.
Assume either
\begin{enumerate}
\item[(a)] $Y^\bullet$ is acyclic, or
\item[(b)] $X^\bullet$ is acyclic.
\end{enumerate}
Then $\Hom^\bullet(X^\bullet,Y^\bullet)$ is acyclic.
\end{lemma}

\begin{proof}
By the remark above, one has only to check that any morphism of $X^\bullet$ to $T^n(Y^\bullet)$ is homotopic to zero, or, since $T^n(Y^\bullet)$ also satisfies the hypotheses of the lemma, it is enough to show that any morphism of $X^\bullet$ to $Y^\bullet$ is homotopic to zero.
In case (a), $Y^\bullet$ is split exact, and it is easy to construct the homotopy (left to reader).
In case (b) the result follows from Lemma~\ref{lem:1.4.4}.
\end{proof}

Suppose $\mathcal{A}$ has enough injectives, and let $\mathcal{L}\subseteq\KK^+(\mathcal{A})$ be the triangulated
subcategory of bounded-below injective complexes.
By Lemma 1.6.2(a), for fixed $X^\bullet\in\KK(\mathcal{A})$, the functor
\[
\Hom^\bullet(X^\bullet,\,\cdot\,)\colon\KK^+(\mathcal{A})\to\KK(\mathbf{Ab})
\]
satisfies the hypotheses of Theorem 1.5.1, hence admits a right derived functor.
This is functorial in $X^\bullet$, giving a bi-$\partial$-functor
\[
\DerR_\mathrm{II}\Hom^\bullet
\colon\KK(\mathcal{A})^\circ \times \DD^+(\mathcal{A}) \to \DD(\mathbf{Ab}).
\]

Now using the lemma, part b), we see that this functor is "exa
in the first variable, i.e., takes acyclic complexes into acyc
complexes, and hence passes to the quotient, giving a trivial
derived functor
\[
\DerR_\mathrm{I}\DerR_\mathrm{II}\Hom^\bullet: \quad D(A)^\circ \times D^+(A) \longrightarrow D(\mathbf{Ab}).
\]
(We will denote this functor by $\DerR\Hom^\bullet$ when no confusion can

Suppose on the other hand that $A$ has enough projectives
by the usual process of "reversing the arrows" we see that the
also a functor
\[
\DerR_\mathrm{II}\DerR_\mathrm{I}\Hom^\bullet: \quad D^-(A)^\circ \times D(A) \longrightarrow D(A) .
\]
Now if $A$ has enough injectives and enough projectives, then
functors $\DerR_\mathrm{I}\DerR_\mathrm{II}\Hom^\bullet$ and $\DerR_\mathrm{II}\DerR_\mathrm{I}\Hom^\bullet$ are defined on $D^-(A)^\circ \times D^+$

and are canonically isomorphic, as we see by the lemma below.
Thus we are justified in using the ambiguous notation $\DerR\Hom^\bullet$.


\begin{lemma}\label{lem:1.6.3}
Let $\mathcal{A},\mathcal{B},\mathcal{C}$ be abelian categories,
\[
T\colon\KK^*(\mathcal{A})\times\KK^\dagger(\mathcal{B})\to\KK(\mathcal{C})
\]
a bi-$\partial$-functor.
Suppose that the derived functors $\DerR_\mathrm{I}\DerR_\mathrm{II}T$ and $\DerR_\mathrm{II}\DerR_\mathrm{I}T$ both exists, (where the subscripts $\mathrm{I},\,\mathrm{II}$ denote the derived functor in the first 
or second variable, respectively). Then there is a unique isomorphism 
between them compatible with the morphisms $\xi_1:T\rightarrow\DerR_\mathrm{I}\DerR_\mathrm{II}T$ and $\xi_2:T\rightarrow\DerR_\mathrm{II}\DerR_\mathrm{I}T$
\end{lemma}

\begin{proof}
Immediate from the universal property of derived functors.
\end{proof}

\begin{theorem}[Yoneda]\label{thm:1.6.4}
Let $\mathcal{A}$ have enough injectives.
For all $X^\bullet\in\DD(\mathcal{A})$, $Y^\bullet\in\DD^+(\mathcal{A})$,
\[
H^i\big(\DerR\Hom^\bullet(X^\bullet,Y^\bullet)\big)
= \operatorname{Ext}^i\big(X^\bullet,Y^\bullet\big).
\]
\end{theorem}

\begin{corollary}\label{cor:1.6.5}
If $\mathcal{A}$ has enough injectives, the derived-category definition of $\operatorname{Ext}^i(X,Y)$
coincides with the classical $\Ext$ groups for all $X,Y\in\mathcal{A}$.
\end{corollary}

\begin{proof}[Proof of Corollary 1.6.5]
Take an injective resolution $I^\bullet$ of $Y$. Then
\[
\operatorname{Ext}^i(X,Y) = H^i\big(\Hom^\bullet(X,I^\bullet)\big),
\]
which is the standard definition.
\end{proof}

\begin{proof}[Proof of Theorem 1.6.4]
Choose a quasi-isomorphism $s\colon Y^\bullet\to I^\bullet$ with $I^\bullet$ a bounded-below injective complex. Then
\[
\operatorname{Ext}^i(X^\bullet,Y^\bullet)
= \operatorname{Ext}^i(X^\bullet,I^\bullet)
= \Hom_{\DD(\mathcal{A})}\big(X^\bullet,T^i(I^\bullet)\big).
\]
By Lemma 1.4.5, one sees that every morphism in $\DD(\mathcal{A)}$ of 
a complex $X"$ to a complex of injectives bounded below, say $T^i(I^\bullet)$, 
is represented by an actual morphism of complexes. Hence the above 
is equal to
\[
\begin{aligned}
\Hom_{\DD(\mathcal{A})}\big(X^\bullet,T^i(I^\bullet)\big)
&= \Hom_{\KK(\mathcal{A})}\big(X^\bullet,T^i(I^\bullet)\big) \\
&= H^i\big(\Hom^\bullet(X^\bullet,I^\bullet)\big) \\
&= H^i\big(\DerR\Hom^\bullet(X^\bullet,Y^\bullet)\big).
\end{aligned}
\]
\end{proof}

\section{Way-out functors and Isomorphisms}

\begin{definition}
Let $\mathcal{A},\mathcal{B}$ be abelian categories, and let $F\colon\DD(\mathcal{A})\to\DD(\mathcal{B})$ be a (covariant) $\partial$-functor.
We say $F$ is \emph{way-out (right)} if for every $n_1\in\mathbb{Z}$, there exists $n_2\in\mathbb{Z}$ such that
for any complex $X^\bullet\in\DD(\mathcal{A})$ satisfying $H^i(X^\bullet)=0$ for all $i<n_2$,
we have $H^i(F(X^\bullet))=0$ for all $i<n_1$.

One defines \emph{way-out left} and \emph{way-out in both directions} similarly.
For a contravariant $\partial$-functor $F\colon\DD(\mathcal{A})\to\DD(\mathcal{B})$,
the definition of way-out right is the same, except reversing the inequality to $i>n_2$.
\end{definition}

\textbf{Examples.}
\begin{enumerate}
\item If $F_0\colon\mathcal{A}\to\mathcal{B}$ is additive and satisfies the hypotheses of Corollary 1.5.3($\alpha$) or ($\beta$),
then $\DerR^+F$ is way-out right.
If $F_0$ satisfies ($\gamma$), then $\DerR F$ is way-out in both directions.

\item For unbounded $X^\bullet\in\DD(\mathcal{A})$, the functor
$\DerR\Hom(X^\bullet,\,Y^\bullet\,)$ for  $Y^\bullet \in \Ob \DD^+(\mathcal{A})$
is generally not way-out in $Y^\bullet$.
\end{enumerate}

\begin{proposition}[Lemma on Way-out Functors]\label{prop:1.7.1}
Let $\mathcal{A},\mathcal{B}$ be abelian categories, $\mathcal{A}'\subseteq\mathcal{A}$ a thick subcategory.
Let $F,G$  be $\partial$-functors from $\DD_{\mathcal{A}'}^+(\mathcal{A})$ or $\DD_{\mathcal{A}'}(\mathcal{A})$ to $\DD(\mathcal{B})$,
and $\eta\colon F\to G$ a morphism of functors.
\begin{enumerate}
\item[(i)] If $\eta(X)$ is an isomorphism for all $X\in\operatorname{Ob}\mathcal{A}'$,
then $\eta(X^\bullet)$ is an isomorphism for all $X^\bullet\in\DD_{\mathcal{A}'}^b(\mathcal{A})$.

\item[(ii)] If $\eta(X)$ is an isomorphism for all $X\in\operatorname{Ob}\mathcal{A}'$,
and $F,G$ are way-out right,
then $\eta(X^\bullet)$ is an isomorphism for all $X^\bullet\in\DD_{\mathcal{A}'}^+(\mathcal{A})$.

\item[(iii)] If $\eta(X)$ is an isomorphism for all $X\in\operatorname{Ob}\mathcal{A}'$,
and $F,G$ are way-out in both directions,
then $\eta(X^\bullet)$ is an isomorphism for all $X^\bullet\in\DD_{\mathcal{A}'}(\mathcal{A})$.

\item[(iv)] Let $P\subseteq\operatorname{Ob}\mathcal{A}'$ be such that every object of $\mathcal{A}'$ embeds into an object of $P$.
If $\eta(X)$ is an isomorphism for all $X\in P$, and $F,G$ are way-out right,
then $\eta(X)$ is an isomorphism for all $X\in\operatorname{Ob}\mathcal{A}'$.
\end{enumerate}
\end{proposition}

\begin{definition}
Let $X^\bullet$ be a complex over abelian category $\mathcal{A}$, $n\in\mathbb{Z}$.
Define truncation functors:
\begin{align*}
\tau_{>n}(X^\bullet)&\colon \cdots\to 0\to X^{n+1}\to X^{n+2}\to\cdots,\\
\tau_{\le n}(X^\bullet)&\colon \cdots\to X^{n-1}\to X^n\to 0\to\cdots,\\
\sigma_{>n}(X^\bullet)&\colon \cdots\to 0\to \operatorname{im}d^n\to X^{n+1}\to X^{n+2}\to\cdots,\\
\sigma_{\le n}(X^\bullet)&\colon \cdots\to X^{n-1}\to \ker d^n\to 0\to\cdots.
\end{align*}

There are natural morphisms inducing short exact sequences of complexes:
\begin{align}
0 &\to \tau_{>n}(X^\bullet) \to X^\bullet \to \tau_{\le n}(X^\bullet) \to 0,\\
0 &\to \sigma_{\le n}(X^\bullet) \to X^\bullet \to \sigma_{>n}(X^\bullet) \to 0.
\end{align}

The $\sigma$-truncations satisfy:
\[
H^i\big(\sigma_{>n}(X^\bullet)\big)
=
\begin{cases}
H^i(X^\bullet) & i>n,\\
0 & i\le n;
\end{cases}
\qquad
H^i\big(\sigma_{\le n}(X^\bullet)\big)
=
\begin{cases}
H^i(X^\bullet) & i\le n,\\
0 & i>n.
\end{cases}
\]
\end{definition}

\begin{lemma}\label{lem:1.7.2}
For any complex $X^\bullet$ over $\mathcal{A}$, there exist triangles in $\DD(\mathcal{A})$:

(3)
\[
\begin{tikzcd}
	& \tau_{>n}(X^\bullet) \arrow[ld] & \\
	\tau_{\geq n}(X^\bullet) \arrow[rr] & & X^n\arrow[lu]
\end{tikzcd}
\]

\vspace{2em}

(4)
\[
\begin{tikzcd}
	& \sigma_{>n}(X^\bullet) \arrow[ld] & \\
	H^n(X^\bullet) \arrow[rr] & & \sigma_{\geq n}(X^\bullet) \arrow[lu]
\end{tikzcd}
\]
\end{lemma}

\begin{proof}
Triangle (3) comes from the short exact sequence
\[
0\to\tau_{>n}(X^\bullet)\to\tau_{\ge n}(X^\bullet)\to X^n\to 0.
\]

For the second, define
$\sigma_{\ge n}'(X^\bullet)$ by
\[
\cdots\to 0\to X^n/\operatorname{im}d^{n-1}\to X^{n+1}\to\cdots.
\]
There is a quasi-isomorphism $\sigma_{\ge n}(X^\bullet)\to\sigma_{\ge n}'(X^\bullet)$,
and an exact sequence
\[
0\to H^n(X^\bullet)\to\sigma_{\ge n}'(X^\bullet)\to\sigma_{>n}(X^\bullet)\to 0.
\]
This induces the required triangle in $\DD(\mathcal{A})$.
\end{proof}

\begin{proof}[Proof of Proposition 1.7.1]
(i) Let $X^\bullet\in\operatorname{Ob}\DD_{\mathcal{A}'}^b(\mathcal{A})$. We prove, by descending induction on $n$, that
\[
\eta\big(\sigma_{>n}(X^\bullet)\big): F(\sigma_{>n}(X^\bullet))\to G(\sigma_{>n}(X^\bullet))
\]
is an isomorphism for all $n$. If $n$ is large enough, then $\sigma_{>n}(X^\bullet)$ has zero cohomology, since $X^\bullet$ has bounded cohomology. Hence it is the zero object of $\DD(\mathcal{A})$, and $\eta$ of it is an isomorphism. The induction step follows from the hypotheses and Proposition 1.1(c), applied to the triangle (4) above. Now for $n$ small enough, the natural map $X^\bullet\to\sigma_{>n}(X^\bullet)$ is a quasi-isomorphism, hence an isomorphism in $\DD(\mathcal{A})$, and we are done.

(ii) Let $X^\bullet\in\operatorname{Ob}\DD_{\mathcal{A}'}^+(\mathcal{A})$. To show $\eta(X^\bullet)$ is an isomorphism, it is sufficient to show that
\[
H^j(\eta(X^\bullet)): H^j(F(X^\bullet))\to H^j(G(X^\bullet))
\]
is an isomorphism for all $j\in\mathbb{Z}$. Given $j$, let $n_1\ge j+2$, and choose $n_2$ as in the definition of way-out functors, to work for $F$ and $G$ both. From the exact sequence (2) above, we have a triangle in $\DD(\mathcal{A})$.
\[
\begin{tikzcd}
	& \tau_{>n_2}(X^\bullet) \arrow[ld] & \\
	\tau_{\geq n_2}(X^\bullet) \arrow[rr] & & X^\bullet\arrow[lu]
\end{tikzcd}
\]
 Since
\[
H^i(\sigma_{>n_2}(X^\bullet))=0 \quad\text{for } i\le n_2,
\]
we have
\[
H^i\big(F(\sigma_{>n_2}(X^\bullet))\big) = 0 = H^i\big(G(\sigma_{>n_2}(X^\bullet))\big)
\]
for $i<n_1$, in particular for $i=j,j+1$. Therefore from the long exact sequence of cohomology we get isomorphisms
\begin{align*}
H^j\big(F(\sigma_{\le n_2}(X^\bullet))\big) &\stackrel{\sim}{\longrightarrow} H^j\big(F(X^\bullet)\big),\\
H^j\big(G(\sigma_{\le n_2}(X^\bullet))\big) &\stackrel{\sim}{\longrightarrow} H^j\big(G(X^\bullet)\big).
\end{align*}
But $\sigma_{\le n_2}(X^\bullet)\in\DD_{\mathcal{A}'}^b(\mathcal{A})$, so $\eta$ is an isomorphism on it by what we have just proved. Hence $H^j(\eta(X^\bullet))$ is an isomorphism, as required.

(iii) Given $X^\bullet\in\DD_{\mathcal{A}'}(\mathcal{A})$, we treat first $\sigma_{\le 0}(X^\bullet)$ and $\sigma_{>0}(X^\bullet)$ by case (ii), then glue the results by a triangle deduced from the exact sequence (2).

(iv) Given $X\in\operatorname{Ob}\mathcal{A}'$, we can find by Lemma 1.4.6 a resolution $I^\bullet\in\DD_{\mathcal{A}'}^+(\mathcal{A})$ of $X$, with each $I^p\in P$. Thus it is sufficient to show that $\eta(I^\bullet)$ is an isomorphism. This follows by applying the technique of (i) and (ii), but using the functors $\tau$ instead of $\sigma$.
\end{proof}

\begin{proposition}\label{prop:1.7.2}
Let $\mathcal{A}$, $\mathcal{B}$ be abelian categories, and let $\mathcal{A}'\subseteq\mathcal{A}$, $\mathcal{B}'\subseteq\mathcal{B}$ be thick abelian subcategories,
$F$ be a $\partial$-functor from $\DD_{\mathcal{A}'}^+(\mathcal{A})$ or $\DD_{\mathcal{A}'}(\mathcal{A})$ to $\DD(\mathcal{B})$,.
\begin{enumerate}
\item[(i)] If $F(X)\in\DD_{\mathcal{B}'}(\mathcal{B})$ for all $X\in\operatorname{Ob}\mathcal{A}'$,
then $F(X^\bullet)\in\DD_{\mathcal{B}'}(\mathcal{B})$ for all $X^\bullet\in\DD_{\mathcal{A}'}^b(\mathcal{A})$.

\item[(ii)] If $F(X)\in\DD_{\mathcal{B}'}(\mathcal{B})$ for all $X\in\operatorname{Ob}\mathcal{A}'$
and $F$ is way-out right,
then $F(X^\bullet)\in\DD_{\mathcal{B}'}(\mathcal{B})$ for all $X^\bullet\in\DD_{\mathcal{A}'}^+(\mathcal{A})$.

\item[(iii)] As in (ii) if $F$ is way-out in both directions, then $F(X^\bullet)\in\DD_{\mathcal{B}'}(\mathcal{B})$ for all $X^\bullet\in\DD_{\mathcal{A}'}(\mathcal{A})$.

\item[(iv)] Let $P\subseteq\operatorname{Ob}\mathcal{A}'$ such that every object of $\mathcal{A}'$ embeds into $P$.
If $F(X)\in\DD_{\mathcal{B}'}(\mathcal{B})$ for all $X\in P$ and $F$ is way-out right,
then $F(X)\in\DD_{\mathcal{B}'}(\mathcal{B})$ for all $X\in\operatorname{Ob}\mathcal{A}'$.
\end{enumerate}
\end{proposition}

\begin{proof}
The proof is analogous to that of the previous 
proposition, and will be left to the reader. 
\end{proof}

\begin{proposition}\label{prop:1.7.4}
Let $\mathcal{A}$ have enough injectives, $F\colon\mathcal{A}\to\mathcal{B}$ additive of cohomological dimension $\le n$.
Let $P\subseteq\operatorname{Ob}\mathcal{A}$ be all $X$ with $\RR^iF(X)=0$ for $i\ne n$.
Assume every object of $\mathcal{A}$ is a quotient of an object in $P$.
Set $G=\RR^nF$. Then $\DerR F,\DerL G$ exist, and there is a functorial isomorphism
\[
\psi\colon \DerR F \stackrel{\sim}{\to} \DerL G[-n],
\]
where $[-n]$ denotes shifting right by $n$ degrees.
\end{proposition}

\begin{proof}
$\DerR F$ exists by Corollary~\ref{cor:1.5.3}.
To see that $\DerL G$ exists, we apply Theorem~\ref{thm:1.5.1} with the arrows reversed.
By hypothesis $P$ satisfies condition (i)$^*$ of Lemma~\ref{lem:1.4.6} (where $*$ denotes reversal of arrows), and one sees easily from the definition of $P$ that it satisfies also (ii)$^*$, (iii)$^*$, and (iv)$^*$ of Corollary~\ref{cor:1.5.3}.
Therefore, if we let $\mathcal{L}\subseteq\KK(\mathcal{A})$ be the triangulated subcategory consisting of complexes of elements of $P$, we see as in the proof of Corollary~\ref{cor:1.5.3}($\gamma$) that the hypotheses 1)$^*$ and 2)$^*$ = 2) of the theorem are satisfied, and so $\DerL G$ exists.

To define the morphism $\psi$, we observe, as in the proof of Theorem~\ref{thm:1.5.1}, that $\mathcal{L}_{\operatorname{Qis}}\to\DD(\mathcal{A})$ is an equivalence of categories, so it will be sufficient to define $\psi$ on $\mathcal{L}_{\operatorname{Qis}}$. Or, using Proposition~\ref{prop:1.3.4}, it will be sufficient to define $\psi$ on $\mathcal{L}$ itself.
In other words, for every complex $X^\bullet$ of objects of $P$ we must give a morphism in $\DD(\mathcal{B})$,
\[
\psi(X^\bullet)\colon \DerR F(X^\bullet)\to \DerL G(X^\bullet)[-n],
\]
such that whenever $f\colon X^\bullet\to Y^\bullet$ is a morphism of such complexes, there is the usual commutative diagram
$\DerL G(f)\cdot\psi(X^\bullet)=\psi(Y^\bullet)\cdot\DerR F(f)$.


\begin{definition}
Let $\mathcal{A}$ be an abelian category, $X^\bullet$ a complex of objects of $\mathcal{A}$. We refer to [M, Ch.~IV, \S4] for the definition of double complexes, maps and homotopies of double complexes, and injective resolutions of complexes. We recall the following facts.
 A \emph{(right) Cartan--Eilenberg resolution} of $X^\bullet$ is a double complex $C^{\cdot\cdot}$ of injective objects of $\mathcal{A}$, with $C^{p,q}=0$ if $p<0$, together with an augmentation morphism $\epsilon\colon X^\bullet\to C^{\bullet,0}$ such that for every $p\in\mathbb{Z}$, the induced maps
\[
B^p(\epsilon)\colon B^p(X^\bullet) \to B^p_{\mathrm{I}}(C^{\cdot\cdot}),\qquad
H^p(\epsilon)\colon H^p(X^\bullet) \to H^p_{\mathrm{I}}(C^{\cdot\cdot})
\]
are injective resolutions in the usual sense (cf.\ [M, Ch.~XVII, \S1] where this is called an injective resolution of $X^\bullet$).
\end{definition}

\begin{lemma}\label{lem:1.7.5}
\leavevmode
\begin{enumerate}
\item[a)] If $\mathcal{A}$ has enough injectives, every complex $X^\bullet$ of objects of $\mathcal{A}$ has a Cartan--Eilenberg resolution.
\item[b)] If $f\colon X^\bullet\to Y^\bullet$ is a morphism of complexes, and $C^{\cdot\cdot},D^{\cdot\cdot}$ are Cartan--Eilenberg resolutions of $X^\bullet,Y^\bullet$, then there exists a map $F\colon C^{\cdot\cdot}\to D^{\cdot\cdot}$ of double complexes lying over $f$.
\item[c)] If $f,g\colon X^\bullet\to Y^\bullet$ are homotopic maps, and $F,G\colon C^{\cdot\cdot}\to D^{\cdot\cdot}$ are maps of Cartan-Eilenberg resolutions lying over $f,g$, then $F$ is homotopic to $G$.
\item[d)] If $F,G\colon C^{\cdot\cdot}\to D^{\cdot\cdot}$ are homotopic maps of double complexes, then $s(F),s(G)\colon s(C^{\cdot\cdot})\to s(D^{\cdot\cdot})$ are homotopic maps of the associated simple complexes.
\item[e)] If $F,G\colon C^{\cdot\cdot}\to D^{\cdot\cdot}$ are homotopic maps of double complexes, and $\sigma^{\mathrm{II}}_{\le n}$ denotes truncation with respect to the second differential $\mathrm{d}_2$, then the restrictions of $F$ and $G$ to maps $\sigma^{\mathrm{II}}_{\le n}(C^{\cdot\cdot})\to\sigma^{\mathrm{II}}_{\le n}(D^{\cdot\cdot})$ are homotopic.
\item[f)] If $\epsilon\colon X^\bullet\to C^{\cdot\cdot}$ augments $X^\bullet$ to a double complex $C^{\cdot\cdot}$ with $C^{p,q}=0$ for $q<0$ and $q>n_0$ (for suitable $n_0$), and such that for each $p$ the map $X^p\to C^{p,\bullet}$ is a resolution, then the natural map $X^\bullet\to s(C^{\cdot\cdot})$ into the associated simple complex is a quasi-isomorphism.
\end{enumerate}
\end{lemma}

\begin{proof}[Proof of Lemma 1.7.5]
Parts a), b), and c) are in [M, Ch.~XVII, Prop.\ 1.2]. Part d) is in [M, Ch.~IV, \S4]. Part e) is easy. Part f) follows either from the spectral sequence of a double complex [EGA~0\textsubscript{III}~11.3.3(ii)] or by a direct calculation.
\end{proof}

\textit{Proof of Proposition 1.7.4, continued.}
Given $X^\bullet\in\operatorname{Ob}\mathcal{L}$, choose a Cartan--Eilenberg resolution $C^{\cdot\cdot}$ of $X^\bullet$ (exists by Lemma 1.7.5 a)). Define $C'^{\cdot\cdot} = \sigma^{\mathrm{II}}_{\le n}(C^{\cdot\cdot})$; explicitly
\[
C'^{p,q}=
\begin{cases}
C^{p,q} & q<n,\\
\ker d_2^{p,n} & q=n,\\
0 & q>n.
\end{cases}
\]

For each $p\in\mathbb{Z}$, we have an exact sequence
\[
0\to X^p\to C'^{p,0}\to C'^{p,1}\to\cdots\to C'^{p,n-1}\to C'^{p,n}\to 0.
\]
The terms $C'^{p,0},\dots,C'^{p,n-1}$ are injective and $X^p\in P$ implies $C'^{p,n}$ is $F$-acyclic. Hence this resolution may be used to calculate $\DerR F(X^p)$ (see end of Theorem 1.5.1), giving an isomorphism
\[
\varphi(t^p)\colon G(X^p)=\RR^nF(X^p) \stackrel{\sim}{\longrightarrow} F(C'^{p,n})\big/\operatorname{im}F(C'^{p,n-1}),
\]
where $t^p$ is the quasi-isomorphism $X^p\to C^{p,\bullet}$. This may be used to construct a map
\[
\alpha^p\colon F(C^{p,\bullet})\to G(X^p),
\]
whence a map of double complexes
\[
\alpha\colon F(C'^{\cdot\cdot})\to G(X^\bullet),
\]
where $G(X^\bullet)$ is concentrated in the $n$-th row.

Passing to the associated simple complexes we obtain
\[
s(\alpha)\colon F\big(s(C'^{\cdot\cdot})\big)\to G(X^\bullet)[-n].
\]
Now $u\colon X^\bullet\to s(C'^{\cdot\cdot})$ is a quasi-isomorphism into a complex of $F$-acyclic objects, by Lemma 1.7.5(f), so there is an isomorphism
\[
\varphi(u)\colon \DerR F(X^\bullet) \stackrel{\sim}{\longrightarrow} F\big(s(C'^{\cdot\cdot})\big).
\]
Since $X^\bullet$ consists of $G$-acyclic objects, there is an isomorphism
\[
\varphi(\operatorname{id}_{X^\bullet})\colon G(X^\bullet) \stackrel{\sim}{\longrightarrow} \DerL G(X^\bullet).
\]
Composing, we define
\[
\psi(X^\bullet)\colon \DerR F(X^\bullet) \longrightarrow \DerL G(X^\bullet)[-n].
\]

I do not care whether  $\psi(X^\bullet)$ is dependent of the choice of the Cartan--Eilenberg resolution $C^{\cdot\cdot}$. It will be sufficient to verify that whenever $f\colon X^\bullet\to Y^\bullet$ is a morphism of complexes in $\mathcal{L}$, then $\psi(X^\bullet)$ and $\psi(Y^\bullet)$ defined as above, fit into a commutative diagram. This is not hard to show using the results of the lemma above, and can safely be left to the reader.

Thus we have a morphism of functors $\psi\colon \DerR F \to \DerL G[-n]$.

To show that $\psi$ is an isomorphism, we note that $\DerR F$ and $\DerL G$ are way-out in both directions, and so, by the lemma on way-out functors (Proposition~\ref{prop:1.7.1}), we reduce to showing $\psi(X)$ is an isomorphism for any $X\in P$. But that is clear from the construction.
\end{proof}

\begin{proposition}\label{prop:1.7.6}
Let $\mathcal{A}$ have enough injectives, $X^\bullet\in\KK^+(\mathcal{A})$. The following are equivalent:
\begin{enumerate}
\item[(i)] $X^\bullet$ admits a quasi-isomorphism $X^\bullet\rightarrow I^\bullet$ into a bounded complex of injective objects of $\mathcal{A}$.
\item[(ii)] The functor $\DerR\Hom(\,\cdot\,,X^\bullet)\colon\DD(\mathcal{A})^\circ\to\DD(\mathbf{Ab})$ is way-out left (hence way-out both ways).
\item[(iii)] There exists $n_0\in\mathbb{Z}$ such that $\operatorname{Ext}^i(Y,X^\bullet)=0$ for all $Y\in\operatorname{Ob}\mathcal{A}$ and all $i>n_0$.
\end{enumerate}
\end{proposition}

\begin{proof}
$(i)\Rightarrow(ii)$: We may assume that $X^\bullet$ is a bounded 
complex of injectives, and calculate $F(Y^\bullet)$ as $\Hom(Y^\bullet,X^\bullet)$. Then 
it is clear that F is way-out in both directions. 


$(ii)\Rightarrow(iii)$: Since $F$ is way-out left, choose $n_0$ such that whenever
$Y^\bullet\in\DD(\mathcal{A})$ and $H^i(Y^\bullet)=0$ for $i<n_0$, then $H^i(F(Y^\bullet))=0$
for $i>0$. Then this $n_0$ will do. Indeed, let $Y\in\operatorname{Ob}\mathcal{A}$,
and let $Y'^\bullet$ be the complex $T^{-n_0}(Y)$. Then $H^i(Y'^\bullet)=0$ for
$i<n_0$, so $H^i(F(Y'^\bullet))=0$ for $i>0$. But
$H^i(F(Y'^\bullet)) = H^i(F(T^{-n_0}Y)) = H^{i+n_0}(F(Y))$.
This says $\operatorname{Ext}^j(Y,X^\bullet)=0$ for $j>n_0$, as required.

\medskip

$(iii)\Rightarrow(i)$: Let $X^\bullet$ satisfy condition (iii) for $n_0$. Since
$\mathcal{A}$ has enough injectives, we can find an injective resolution of
$X^\bullet$ (Lemma~\ref{lem:1.4.6}), i.e., a quasi-isomorphism
$s\colon X^\bullet\to X'^\bullet$ where $X'^\bullet$ is a bounded-below complex
of injective objects of $\mathcal{A}$.

I claim that $H^i(X'^\bullet)=0$ for all $i>n_0$. Suppose to the contrary
that $H^m(X'^\bullet)\neq 0$ for some $m>n_0$. Then from the exact sequence
\[
0 \to B^m(X'^\bullet) \to Z^m(X'^\bullet) \to H^m(X'^\bullet) \to 0
\]
we see that the first inclusion is strict. Hence there exists a
$Y\in\operatorname{Ob}\mathcal{A}$ (e.g., $Y=Z^m(X'^\bullet)$) such that the inclusion
\[
\Hom(Y, B^m(X'^\bullet)) \to \Hom(Y, Z^m(X'^\bullet))
\]
is strict. However, there is a commutative diagram
\[
\begin{CD}
\Hom(Y,B^m(X'^\bullet)) @>>> \Hom(Y,Z^m(X'^\bullet)) \\
@VVV @VV{\cong}V \\
B^m\big(\Hom^\bullet(Y,X'^\bullet)\big) @>>> Z^m\big(\Hom^\bullet(Y,X'^\bullet)\big)
\end{CD}
\]
with an isomorphism on the right since $\Hom$ is left exact.
But by hypothesis $\operatorname{Ext}^m(Y,X^\bullet) = H^m(\Hom^\bullet(Y,X'^\bullet)) = 0$,
so the arrow on top is an isomorphism, which gives a contradiction.
Hence $H^i(X'^\bullet)=0$ for $i>n_0$, as claimed.

It follows that the map
\[
i\colon \sigma_{\le n}(X'^\bullet) \to X'^\bullet
\]
is a quasi-isomorphism for any $n\ge n_0$ (using the notation introduced
earlier in this section). Now I claim that
$Z^{n+1}(X'^\bullet)=B^{n+1}(X'^\bullet)$ is injective for any $n\ge n_0$.
This will show that $\sigma_{\le n+1}(X'^\bullet)$ is a bounded complex of
injectives.

Consider the exact sequence of complexes
\[
0 \to \sigma_{\le n}(X'^\bullet) \to \tau_{\le n}(X'^\bullet) \to B^{n+1}(X'^\bullet)[-n] \to 0
\]
for $n\ge n_0$. We will show that $B^{n+1}=B^{n+1}(X'^\bullet)$ is injective by
showing that $\operatorname{Ext}^1(Y,B^{n+1})=0$ for all $Y\in\operatorname{Ob}\mathcal{A}$.
For any $Y$, we have
\[
\operatorname{Ext}^1(Y,B^{n+1}) = \operatorname{Ext}^{\,n+1}\big(Y,B^{n+1}[-n]\big)
\]
and there is an exact sequence
\[
\cdots \to \operatorname{Ext}^{n+1}\big(Y,\tau_{\le n}(X'^\bullet)\big)
\to \operatorname{Ext}^{n+1}\big(Y,B^{n+1}[-n]\big)
\to \operatorname{Ext}^{n+2}\big(Y,\sigma_{\le n}(X'^\bullet)\big) \to \cdots
\]
The group on the left is zero since $\tau_{\le n}(X'^\bullet)$ is an injective
complex which stops in degree $n$. The group on the right is zero by
our hypothesis and the fact that $\sigma_{\le n}(X'^\bullet)$ is isomorphic to
$X'^\bullet$ in $\DD^+(\mathcal{A})$. Hence the middle group is zero.

Now for $n\ge n_0$ we have seen that $\sigma_{\le n}(X'^\bullet)$ is a bounded
complex of injectives, and that the map
\[
i\colon \sigma_{\le n}(X'^\bullet) \to X'^\bullet
\]
is a quasi-isomorphism. By Lemma~\ref{lem:1.4.5}, $i$ has a homotopy inverse,
say $f$. Therefore the composition
\[
fs\colon X^\bullet \to \sigma_{\le n}(X'^\bullet)
\]
gives the required quasi-isomorphism of $X^\bullet$ into a bounded complex
of injectives.
\end{proof}

\begin{definition}
If $X^\bullet\in\KK^+(\mathcal{A})$ satisfies the equivalent conditions of Proposition 1.7.6, we say $X^\bullet$ has \emph{finite injective dimension}.
\end{definition}

\begin{corollary}\label{cor:1.7.7}
The complexes of finite injective dimension form a triangulated localizing subcategory of $\KK(\mathcal{A})$.
\end{corollary}

\begin{proof}
The fact that they form a triangulated subcategory follows e.g.\ from condition (iii) of Proposition~\ref{prop:1.7.6} and the long exact sequence of $\operatorname{Ext}$. We see that the subcategory is localizing by applying Proposition~\ref{prop:1.3.3}(i), since anything in $\KK^+(\mathcal{A})$ quasi-isomorphic to an element of the subcategory is already in the subcategory, and $\KK^+(\mathcal{A})$ is a localizing subcategory of $\KK(\mathcal{A})$.
\end{proof}

\begin{definition}
Denote by $\KK^+(\mathcal{A})_{\mathrm{fid}}$ the full subcategory of $\KK^+(\mathcal{A})$ consisting of complexes of finite injective dimension. The corresponding derived subcategory is $\DD^+(\mathcal{A})_{\mathrm{fid}}$.
\end{definition}

\textbf{Remark.}
These subcategories are essentially different from the subcategories of the form $\KK_{\mathcal{A}'}(\mathcal{A})$ and $\DD_{\mathcal{A}'}(\mathcal{A})$ we have considered before, because they cannot be characterized by putting conditions on the cohomology objects $H^i(X^\bullet)$.
