\chapter{The Derived Category}

\section{Introduction}
Let \(\mathcal{A}\) and \(\mathcal{B}\) be abelian categories, and let \(F\colon \mathcal{A}\to\mathcal{B}\) be a functor. Our purpose is to define, functorially for each \(X\in\operatorname{Ob}\mathcal{A}\), a complex \(\mathbb{R}F(X)\) whose cohomology groups are the right derived functors of \(F\) acting on \(X\), namely \(R^iF(X)\). In general, we will define \(\mathbb{R}F(X^\bullet)\) for any complex \(X^\bullet\) of objects of \(\mathcal{A}\).

More precisely, \(\mathbb{R}F\) will be a functor from the derived category \(\mathcal{D}(\mathcal{A})\) of \(\mathcal{A}\) to the derived category \(\mathcal{D}(\mathcal{B})\) of \(\mathcal{B}\).

The derived category \(\mathcal{D}(\mathcal{A})\) is obtained as follows: one first considers the category \(\mathcal{K}(\mathcal{A})\), whose objects are complexes of elements of \(\mathcal{A}\), and whose morphisms are homotopy equivalence classes of morphisms of complexes. The category \(\mathcal{D}(\mathcal{A})\) is obtained by ``localizing'' \(\mathcal{K}(\mathcal{A})\) so that every morphism in \(\mathcal{K}(\mathcal{A})\) which induces an isomorphism on cohomology becomes an isomorphism in \(\mathcal{D}(\mathcal{A})\). This process of localization will be explained in general below.

Although \(\mathcal{A}\) and \(\mathcal{B}\) above are assumed to be abelian categories, the categories \(\mathcal{K}(\mathcal{A})\), \(\mathcal{D}(\mathcal{A})\), etc., are in general not abelian. However, they can be given a structure which carries enough information for our purposes, namely a structure of triangulated category. Thus we will be led to study triangulated categories.

\section{Triangulated Categories}
\subsection{Definition}
A triangulated category is an additive category \(\mathcal{C}\), together with
\begin{enumerate}
	\item[a)] an automorphism \(T\colon \mathcal{C}\to\mathcal{C}\) called the \emph{translation functor}, and
	\item[b)] a collection of sextuples \((X,Y,Z,u,v,w)\), called the \emph{triangles} of \(\mathcal{C}\),
\end{enumerate}
where in each sextuple \(X,Y,Z\in\operatorname{Ob}\mathcal{C}\) and
\[
u\colon X\to Y,\quad v\colon Y\to Z,\quad w\colon Z\to T(X)
\]
are morphisms. A triangle is usually written
\[
X\xrightarrow{u} Y\xrightarrow{v} Z\xrightarrow{w} T(X).
\]

A morphism of triangles
\[
(X,Y,Z,u,v,w)\to(X',Y',Z',u',v',w')
\]
is a commutative diagram
\[
\begin{CD}
	X @>u>> Y @>v>> Z @>w>> T(X) \\
	@VfVV @VgVV @VhVV @VT(f)VV \\
	X' @>u'>> Y' @>v'>> Z' @>w'>> T(X')
\end{CD}
\]

This data is subject to the following axioms:

\begin{enumerate}
	\item[\textbf{(TR1)}]
	\begin{enumerate}
		\item Every sextuple isomorphic to a triangle is a triangle.
		\item Every morphism \(u\colon X\to Y\) can be embedded in a triangle.
		\item The sextuple \((X,X,0,\operatorname{id}_X,0,0)\) is a triangle.
	\end{enumerate}
	
	\item[\textbf{(TR2)}]
	\((X,Y,Z,u,v,w)\) is a triangle if and only if \((Y,Z,T(X),v,w,-T(u))\) is a triangle.
	
	\item[\textbf{(TR3)}]
	Given two triangles \((X,Y,Z,u,v,w)\) and \((X',Y',Z',u',v',w')\), and morphisms \(f\colon X\to X'\), \(g\colon Y\to Y'\) such that \(u'f=gu\), there exists a morphism \(h\colon Z\to Z'\) (not necessarily unique) so that \((f,g,h)\) is a morphism of triangles.
	
	\item[\textbf{(TR4)}] (The octahedral axiom.)\\
	\begin{center}
	\begin{tikzcd}
		& Y' \arrow[dr, dashed, "g"] & \\
		Z' \arrow[ur, dashed, "f"] \arrow[d] & & X' \arrow[ll, "T(j)i"] \arrow[d] \\
		X \arrow[rr, "vu"] \arrow[dr, "u"'] \arrow[uur, "j" near start] & & Z \arrow[u] \arrow[dl, "v"'] \arrow[uul, "i" near start] \\
		& Y \arrow[uul] \arrow[uur] & 
	\end{tikzcd}
	\end{center}
	
	Suppose given triangles
	\[
	\begin{gathered}
		(X,Y,Z',u,j,\cdot),\\
		(Y,Z,X',v,\cdot,i),\\
		(X,Z,Y',vu,\cdot,\cdot)
	\end{gathered}
	\]
	such that
	\[
	(Z',Y',X',f,g,T(j)i)
	\]
	is a triangle. Then there exist morphisms \(f\colon Z'\to Y'\) and \(g\colon Y'\to X'\) such that the two other faces of the octahedron with \(f,g\) as edges are commutative diagrams.
\end{enumerate}

\begin{definition}
	An additive functor \(F\colon \mathcal{C}\to\mathcal{C}'\) from one triangulated category to another is called a \emph{(covariant) \(\partial\)-functor} if it commutes with the translation functor and takes triangles into triangles. A contravariant \(\partial\)-functor takes triangles into triangles with the arrows reversed and sends the translation functor into its inverse.
\end{definition}

\begin{definition}
	An additive functor \(H\colon \mathcal{C}\to\mathcal{A}\) from a triangulated category to an abelian category is called a \emph{covariant cohomological functor} if whenever \((X,Y,Z,u,v,w)\) is a triangle, the long sequence
	\[
	\cdots\to H(T^iX)\to H(T^iY)\to H(T^iZ)\to H(T^{i+1}X)\to\cdots
	\]
	is exact (the morphisms being \(H(T^iu)\), etc.). If \(H\) is a cohomological functor, we often write \(H^i(X)\) for \(H(T^iX)\), \(i\in\mathbb{Z}\). One defines a contravariant cohomological functor by reversing the arrows.
\end{definition}

\begin{proposition}\label{prop:1.1}
	\begin{enumerate}
		\item[a)] The composition of any two consecutive morphisms in a triangle is zero.
		\item[b)] If \(\mathcal{C}\) is a triangulated category and \(M\) an object of \(\mathcal{C}\), then \(\operatorname{Hom}_{\mathcal{C}}(M,\cdot)\) and \(\operatorname{Hom}_{\mathcal{C}}(\cdot,M)\) are cohomological functors on \(\mathcal{C}\).
		\item[c)] If in the situation of (TR3) \(f\) and \(g\) are isomorphisms, then \(h\) is also an isomorphism.
	\end{enumerate}
\end{proposition}

\begin{proof}
	a) Let \((X,Y,Z,u,v,w)\) be a triangle. By (TR2) it is sufficient to show that \(vu=0\). By (TR1), \((Z,Z,0,\operatorname{id}_Z,0,0)\) is a triangle. Also by (TR2), \((Y,Z,T(X),v,w,-T(u))\) is a triangle. We apply (TR3) to the maps \(v\colon Y\to Z\) and \(\operatorname{id}_Z\colon Z\to Z\), giving a morphism of triangles. It follows that \(T(v)(-T(u))=0\), or since \(T\) is an automorphism, \(vu=0\).
	
	b) Let \((X,Y,Z,u,v,w)\) be a triangle. To show \(\operatorname{Hom}_{\mathcal{C}}(M,\cdot)\) is a cohomological functor, it suffices by (TR2) to show the sequence
	\[
	\operatorname{Hom}_{\mathcal{C}}(M,X)\to\operatorname{Hom}_{\mathcal{C}}(M,Y)\to\operatorname{Hom}_{\mathcal{C}}(M,Z)
	\]
	is exact. By a) we know the composition is zero. Now suppose given \(g\in\operatorname{Hom}_{\mathcal{C}}(M,Y)\) such that \(vg=0\). We apply (TR3) to the triangles \((M,M,0,\operatorname{id}_M,0,0)\) and \((X,Y,Z,u,v,w)\) and the map \(g\colon M\to Y\) to conclude there exists \(f\colon M\to X\) such that \(uf=g\).
	
	A similar proof shows that \(\operatorname{Hom}_{\mathcal{C}}(\cdot,M)\) is a contravariant cohomological functor.
	
	c) In the situation of (TR3), suppose \(f,g\) are isomorphisms. Apply the cohomological functor \(\operatorname{Hom}_{\mathcal{C}}(Z',\cdot)\) to obtain an exact commutative diagram where \(f_*,g_*,T(f)_*,T(g)_*\) are isomorphisms of abelian groups. By the five-lemma, \(h_*\) is an isomorphism. Hence there exists \(\varphi\in\operatorname{Hom}_{\mathcal{C}}(Z',Z)\) such that \(h\varphi=\operatorname{id}_Z\). Using \(\operatorname{Hom}_{\mathcal{C}}(\cdot,Z)\) similarly gives \(\psi\in\operatorname{Hom}_{\mathcal{C}}(Z,Z')\) such that \(\psi h=\operatorname{id}_{Z'}\). Thus \(h\) is an isomorphism.
\end{proof}

\section{\(\mathcal{K}(\mathcal{A})\) is triangulated}
Let \(\mathcal{A}\) be an abelian category. A \emph{complex} of objects of \(\mathcal{A}\) is a collection \(X^\bullet=(X^n)_{n\in\mathbb{Z}}\) of objects of \(\mathcal{A}\) together with maps \(d^n\colon X^n\to X^{n+1}\) such that \(d^{n+1}d^n=0\) for all \(n\in\mathbb{Z}\).

A morphism \(f\) of complexes \(X^\bullet\to Y^\bullet\) is a collection of maps \(f^n\colon X^n\to Y^n\) which commute with differentials:
\[
f^{n+1}d_X^n = d_Y^n f^n
\]
for all \(n\).

Two maps \(f,g\colon X^\bullet\to Y^\bullet\) are \emph{homotopic} if there exists a collection of maps \(k=(k^n)\), \(k^n\colon X^n\to X^{n-1}\) (not necessarily commuting with \(d\)) such that
\[
f^n - g^n = d_Y^{n-1}k^n + k^{n+1}d_X^n
\]
for all \(n\). Homotopy is an equivalence relation, and compositions of homotopic maps are homotopic.

We define \(\mathcal{K}(\mathcal{A})\) to be the category whose objects are complexes of objects of \(\mathcal{A}\), and whose morphisms are homotopy equivalence classes of morphisms of complexes.

A complex \(X^\bullet\) is \emph{bounded below} if \(X^n=0\) for \(n\ll0\). We denote by \(\mathcal{K}^+(\mathcal{A})\) the full subcategory of \(\mathcal{K}(\mathcal{A})\) of complexes bounded below. Similarly we define \(\mathcal{K}^-(\mathcal{A})\) (bounded above) and \(\mathcal{K}^b(\mathcal{A})\) (bounded on both sides).

We now define a triangulated structure on \(\mathcal{K}(\mathcal{A})\) (resp.\ \(\mathcal{K}^+(\mathcal{A})\), etc.). Let \(T\) be the left shift functor with sign change:
\[
T(X^\bullet)^p = X^{p+1},\qquad d_{T(X)} = -d_X.
\]
We often write \(X^\bullet[1]\) instead of \(T(X^\bullet)\), and \(X^\bullet[n]\) instead of \(T^n(X^\bullet)\).

If \(u\colon X^\bullet\to Y^\bullet\) is any morphism, consider its \emph{mapping cone} \(Z^\bullet\), defined as the complex
\[
Z^\bullet = T(X^\bullet)\oplus Y^\bullet
\]
with differential
\[
d_Z = \begin{pmatrix} T(d_X) & T(u) \\ 0 & d_Y \end{pmatrix}.
\]
There are natural morphisms
\[
v\colon Y^\bullet\to Z^\bullet,\qquad w\colon Z^\bullet\to T(X^\bullet).
\]

We define a triangle in \(\mathcal{K}(\mathcal{A})\) to be any sextuple isomorphic to one obtained from a morphism \(u\) by this construction.

All axioms (TR1)--(TR4) are easily verified, once one notes that the mapping cone of \(\operatorname{id}_{X^\bullet}\) is homotopic to \(0\). Indeed, the matrix
\[
k = \begin{pmatrix} 0 & 0 \\ \operatorname{id}_X & 0 \end{pmatrix}
\]
gives a contraction homotopy.

\begin{definition}
	We define \(H\) to be the functor from \(\mathcal{K}(\mathcal{A})\) to \(\mathcal{A}\) which sends a complex \(X^\bullet\) to its \(0^\text{th}\) cohomology:
	\[
	H(X^\bullet) = \ker d^0 \big/ \operatorname{im} d^{-1}.
	\]
	This is indeed a functor, since homotopic maps induce the same map on cohomology. We write \(H^i = H\circ T^i\) for any \(i\in\mathbb{Z}\).
\end{definition}

Observe that \(H\) is a cohomological functor from \(\mathcal{K}(\mathcal{A})\) to \(\mathcal{A}\). Indeed, it suffices to check the long exact sequence for triangles coming from mapping cones, which is straightforward.

\section{$\mathcal{K}(\mathcal{A})$ is triangulated}
\section{Localization of categories}
\section{Quasi-isomorphisms and the derived category}
\section{Way-out functors and isomorphisms}
\section{Examples. $\mathrm{Ext}$ and $R\mathcal{H}\mathit{om}$}
\section{Derived functors}
