This chapter consists for a great part in definitions, which generalize those of the Local Cohomology lecture notes [LC]. Notable new material is the spectral sequence of a filtered topological space, and the Cousin complex of a sheaf.

\section{Local cohomology groups, sheaves, and complexes}

Throughout this section, \(X\) will be an arbitrary topological space, and \(F\) a sheaf of abelian groups on \(X\). There are three ways in which one can vary the basic definition of the cohomology of \(F\) with supports in a closed subset \(Z\) of \(X\): one can replace \(Z\) by a family of supports; one can define a relative local cohomology if \(z' \subseteq z\) are two closed subsets; and one can make everything local by sheafifying. Therefore we will present the definitions in the form of a theme and variations, to allow for all possible combinations of the generalizations suggested above.

We state our results mostly in terms of the cohomology groups, and leave to the reader the appropriate statements in terms of the derived category. When \(X\) is an arbitrary

\setcounter{page}{216}
topological space, we work in the derived category \(D(\cat{Ab}(X))\) of the category of abelian sheaves on \(X\). If \(X\) is a prescheme, we work in the derived category \(D(\operatorname{Mod}(X))\) of \(\sheaf{O}_X\)-modules. All the derived functors considered in this chapter are compatible in the two cases with the natural functor of the category
\[D^{+}(X) \to D^{+}(\cat{Ab}(X)),\]
since any injective \(\sheaf{O}_X\)-module is flasque, and flasque sheaves are acyclic for the functors considered (Motif C below).

\subsection{Theme}
Let \(Z\) be a closed subset of \(X\). Define \(\Gamma_{Z}(X, F)\) to be the group consisting of those global sections of \(F\) whose support lies in \(Z\). Define \(H_{Z}^{i}(X, F)\) to be the \(i^{\text{th}}\) right derived functor of \(\Gamma_{Z}\), and define \(\RGamma_{Z}\) to be the right derived functor on the derived category \(D^{+}(\cat{Ab}(X))\). These are called the local cohomology groups of \(F\) with supports in \(Z\). They have the following properties:

\begin{motif}
If 
\[0 \to F' \to F \to F'' \to 0\]
is a short exact sequence of abelian sheaves on \(X\), then there

\setcounter{page}{217}
is a long exact sequence of groups 
\[0 \to \Gamma_{Z}\left(X, F'\right) \to \Gamma_{Z}(X, F) \to \Gamma_{Z}(X, F'') \to\]
\[H_{Z}^{1}\left(X, F'\right) \to H_{Z}^{1}(X, F) \to H_{Z}^{1}\left(X, F''\right) \to \cdots .\]
\end{motif}
\begin{proof}
This is the same as to say that \(\Gamma_{Z}\) is left exact, and so is equal to \(H^{\circ}(\RGamma_{Z})\) which it is.
\end{proof}

\begin{motif}
There is a long exact sequence 
\[0 \to \Gamma_{Z}(X, F) \to \Gamma(X, F) \to \Gamma(X-Z, F) \to\]
\[H_{Z}^{1}(X, F) \to H^{1}(X, F) \to H^{1}(X-Z, F) \to H_{Z}^{2}(X, F) \to \cdots .\]
\end{motif}
\begin{proof}
For any sheaf \(F\) one has an exact sequence
\[0 \to \Gamma_{Z}(X, F) \to \Gamma(X, F) \to \Gamma(X-Z, F),\]
and if \(F\) is flasque (in particular if \(F\) is injective) one can write a zero on the right. Thus if \(I^\bullet\) is an injective resolution of \(F\), we have an exact sequence of complexes 
\[0 \to \Gamma_{Z}\left(X, I^{\bullet}\right) \to \Gamma\left(X, I^{\bullet}\right) \to \Gamma\left(X-I^{\bullet}, F\right) \to 0\]
which gives rise to a triangle in \(D^+(\cat{Ab})\),

\setcounter{page}{218}
\[\RGamma(X-Z,F) \to \RGamma_Z(X,F) \to \RGamma(X,F)\]
Taking cohomology gives the result.
\end{proof}

\begin{motif}
For \(F\) flasque, and \(i>0\), \(H_{Z}^{i}(X, F)=0\)
\end{motif}
\begin{proof}
This follows from Motif B, and the fact that \(H^{i}(X, F)=H^{i}(X-Z, F)=0\) for \(i>0\), and \(\Gamma(X, F) \to \Gamma(X-Z, F)\) is surjective for \(F\) flasque.
\end{motif}

\begin{remark}
In fact, \(F\) is flasque subspace \(Z\) of \(X\), \(H_{Z}^{1}(X, F)=0\) [LC, 1.10].
\end{remark}

\subsection{Variation 1}
\begin{definition}
A family of supports on a topological space \(X\) is a set \(\varphi\) of closed subsets of \(X\) such that
(a)if \(z \in \varphi\), and \(z'\) is a closed subset of \(z\), then \(Z' \in \varphi\),
(b)if \(z_{1}, z_{2} \in \varphi\), then \(z_{1} \cup z_{2} \in \varphi\)
\end{definition}

Now let \(\varphi\) be a family of supports, and define \(\Gamma_{\varphi}(X, F)\) to be the group of global sections of \(F\) whose support is in \(\varphi\). Define \(\RGamma_{\varphi}(X, F)\) and \(H_{\varphi}^{i}(X, F)\) to be the right derived functors.

\setcounter{page}{219}
\begin{motif}
Repeat as above, with \(Z\) replaced by \(\varphi\).
\end{motif}

\begin{motif}
\[H_{\varphi}^{i}(X, F)=\varinjlim_{Z \in \varphi} H_{Z}^{i}(X, F) .\]
\end{motif}
\begin{proof}
It is true for \(i=0\), and direct limits commute with cohomology of complexes.
\end{proof}

\begin{motif}
For \(F\) flasque, and \(i>0\), \(H_{\varphi}^{i}(X, F)=0\)
\end{motif}
\begin{proof}
Follows from Motif D, and Motif C above.
\end{proof}

\subsection{Variation 2}
Let \(z' \subseteq z\) be closed subsets of \(X\). Define \(\Gamma_{z/z'}(X, F)\) to be \(\Gamma_{z}(X, F) / \Gamma_{z'}(X, F)\).
Define \(\RGamma_{z/z'}\) and \(H_{z/z'}^{i}\) to be the right derived functors.

Note that in general \(\Gamma_{z/z'}\) is not left exact, so that \(\Gamma_{z/z'} \ne H_{z/z'}^{\circ}\)

\begin{motif}
Repeat with \(H^{\circ}\) in place of \(\Gamma\), and \(z / z'\) in place of \(Z\).
\end{motif}

\begin{motif}
There is a long exact sequence 
\[0 \to \Gamma_{z'}(X, F) \to \Gamma_{z}(X, F) \to H_{z/z'}^{\circ}(X, F) \to\]
\[H_{z'}^{1}(X, F) \to H_{z}^{1}(X, F) \to H_{z/z'}^{1}(X, F) \to\]
\[H_{z'}^{2}(X, F) \to \cdots .\]
\end{motif}

\begin{motif}
Repeat.
\end{motif}

\setcounter{page}{220}
\subsection{Variation 3}
Let \(Z\) be a closed subset of \(X\). Define \(\underline{\Gamma}_{Z}(F)\) to be the sheaf whose sections over an open set \(U\) are the elements of \(\Gamma_{Z \cap U}(U,F|_{U})\).
Define \(\mathbf{R}\underline{\Gamma}_{Z}(F)\) and \(\underline{H}_{Z}^{i}(F)\) to be the right derived functors, which are now complexes of sheaves, resp. sheaves on \(X\).

\begin{motif}
Repeat with underlines.
\end{motif}

\begin{motif}
There is a four-term exact sequence 
\[0 \to \underline{\Gamma}_{z}(F) \to F \to j_{*}\left(\left.F\right|_{X-Z}\right) \to \underline{H}_{Z}^{1}(F) \to 0\]
where \(j: X-Z \to X\) is the inclusion and for \(i>0\), there are isomorphisms 
\[R^{i} j_{*}\left(\left.F\right|_{X-Z}\right) \stackrel{\sim}{\to} \underline{H}_{Z}^{i+1}(F) .\]
\end{motif}

\begin{motif}
For \(F\) flasque and \(i>0\), \(\underline{H}_{Z}^{i}(F)=0\)
\end{motif}
\begin{proof}
One sees easily that \(\underline{H}_{Z}^{i}(F)\) is the sheaf associated to the presheaf 
\[U \to H_{Z \cap U}^{i}\left(U,\left.F\right|_{U}\right) .\]
Now since the restriction of a flasque sheaf to an open subset is flasque, the result follows from Motif C above.
\end{proof}

\setcounter{page}{221}
\begin{motif}
There is a spectral sequence 
\[E_{2}^{p q}=H^{p}\left(X, \underline{H}_{Z}^{q}(F)\right) \Rightarrow E^{n}=H_{Z}^{n}(X, F),\]
or equivalently, in terms of the derived categories, \(\RGamma_{Z}=\RGamma \circ \mathbf{R}\underline{\Gamma}_{Z}\)
\end{motif}
\begin{proof}
Referring to [I.5.4], we need only show that \(\underline{\Gamma}_{z}\) takes injectives into \(F\)-acyclic objects. Indeed, any injective is flasque, and \(\Gamma_{z}\) of a flasque is flasque, and any flasque is \(F\)-acyclic.
\end{proof}

\subsection{Variation 4}
Combining variations 1 and 2, let \(\psi \subseteq \varphi\) be two families of supports. Define \(\Gamma_{\varphi / \psi}(X, F)\) and its derived functors \(\RGamma_{\varphi / \psi}\) and \(H_{\varphi / \psi}^{i}\)

\begin{motif}
Repeat.
\end{motif}
\begin{motif}
Repeat.
\end{motif}
\begin{motif}
Repeat.
\end{motif}
\begin{motif}
\[H_{\varphi / \psi}^{i}(X, F)=\varinjlim_{\substack{z \in \varphi \\ z' \in \psi \\ z' \subseteq z}} H_{z / z'}^{i}(X) .\]
\end{motif}
Repeat.

\end{document}